---
title: "Climate Crisis Iteration 2-b-3 (Heating) Endogeneity Evaluation"
output:
  distill::distill_article:
    toc: true
    toc_depth: 1
---

```{r setup, echo =FALSE, include=FALSE}
# Include libraries
library(tidyverse)
library(seminr)
library(DT)
library(htmltools)
library(lmtest)
library(nortest)
library(car)
library(distill)
library(targets)
source(here::here("R", "02_sem-evaluation.R"))
# Load models
tar_config_set(here::here("_targets"))
model <- tar_read("cc_model_2_b_2")
proxymodel <- tar_read("cc_model_2_b_2_proxy")
# Make summaries
summo <- summary(model)
sumprmo <- summary(proxymodel)
```

The code for the assessment of endogeneity using the Gaussian Copula approach comes from

Hult, G. T. M., J. F. Hair, D. Proksch, M. Sarstedt, A. Pinkwart, & C. M. Ringle (2018).
Addressing Endogeneity in International Marketing Applications of Partial Least Squares Structural Equation Modeling. Journal of International Marketing, 26(3), 1–21. https://doi.org/10.1509/jim.17.0151


# Test of parametricity

The Gaussian Copula approach can only be used if the independent variable in question is not normally distributed.
So we first test the distribution of the construct scores.
A significant p value (p < 0.05) for either the Shapiro-Wilk or the Lilliefors test indicates that the data is not normally distributed.

```{r distribution test, echo = FALSE}
# Find out if independent (i.e., exogenous) variables are non-normally distributed
# If yes, Gaussian Copula approach can be used.
testlist <- c(rownames(summo$paths)[-c(1:2)])
nntest <- data.frame('Variable' = character(),
             'Shapiro-Wilk W' = double(),
             'Shapiro Wilk p' = double(),
             'Lilliefors D' = double(),
             'Lilliefors p' = double())
for (i in 1:length(testlist)) {
  nntest <- nntest %>% base::rbind(nonnormaltest(model, testlist[i]),
                             deparse.level = 0)
}
nntest %>%
  datatable(
    caption = 'Results of normality tests',
    rownames = FALSE,
    options = list(pageLength = nrow(nntest))
  ) %>%
  formatRound(-1,
              digits = 3)
```
```{r distribution graph, echo = FALSE}
for (i in 1:length(testlist)) {
  nonnormalgraph(model, testlist[i])
}
```



All independent (or endogenous) variables are non-normally distributed.
Therefore, the Gaussian Copula approach can be used for all of them.


# Regression of Response Beliefs on Distrusting Beliefs and Knowledge

```{r gca rb, echo = FALSE, include = FALSE}
# Define Variables for easy access
KN <- model$construct_scores[,"Knowledge"]
DI <- model$construct_scores[,"Distrusting Beliefs"]
RB <- model$construct_scores[,"Response Beliefs"]

# Define number of bootstraps: 10.000 for reporting, 100 for testing
bootrounds <- 10000

# Estimate regression model
rbmodel <- lm(RB ~ DI + KN)
summary(rbmodel)
bootrb <- Boot(rbmodel, R=bootrounds)
summary(bootrb)

# Make base df
rbdf <- data.frame(Construct = c("Distrusting Beliefs", "Knowledge", "Copula Distrusting Beliefs", "Copula Knowledge"), 
                   Original.Model.Value = c(summary(bootrb)[2:3,5],NA,NA),
                   Original.Model.p = c(bootSig(model$data, bootrb, 2, 0)[2:3],NA,NA)
)

# Calculate copulas for independent variables
KN_star <- createCopula(KN)
DI_star <- createCopula(DI)


# Calculate results with copula for Distrusting Beliefs
# Input is regular model + copula + 0
copuladirb <- lm(RB ~ DI + KN + DI_star + 0)
summary(copuladirb)
# Bootstrap Standard Errors
bootcopuladirb <- Boot(copuladirb, R=bootrounds)
summary(bootcopuladirb)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopuladirb, 2,1)
# Attach to df
rbdf <- rbdf %>% cbind(
  DI.Co.Model.Value = c(summary(bootcopuladirb)[1:3,5], NA),
  DI.Co.Model.p = c(bootSig(model$data, bootcopuladirb, 2,1), NA)
)

# Calculate results with copula for Knowledge
# Input is regular model + copula + 0
copulaknrb <- lm(RB ~ DI + KN + KN_star + 0)
summary(copulaknrb)
# Bootstrap Standard Errors
bootcopulaknrb <- Boot(copulaknrb, R=bootrounds)
summary(bootcopulaknrb)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopulaknrb, 2,1)
# Attach to df
rbdf <- rbdf %>% cbind(
  KN.Co.Model.Value = c(summary(bootcopulaknrb)[1:2,5], NA, summary(bootcopulaknrb)[3,5]),
  KN.Co.Model.p = c(bootSig(model$data, bootcopuladirb, 2,1)[1:2], NA, bootSig(model$data, bootcopuladirb, 3,1)[3])
)

# Calculate results with copula for both DI and KN
# Input is regular model + copula + 0
copuladiknrb <- lm(RB ~ DI + KN + DI_star + KN_star + 0)
summary(copuladiknrb)
# Bootstrap Standard Errors
bootcopuladiknrb <- Boot(copuladiknrb, R=bootrounds)
summary(bootcopuladiknrb)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootstrappedSignificance(model$data, bootcopuladiknrb, 2, 2)
# Attach to df
rbdf <- rbdf %>% cbind(
  DIKN.Co.Model.Value = c(summary(bootcopuladiknrb)[1:4,5]),
  DIKN.Co.Model.p = c(bootSig(model$data, bootcopuladiknrb, 2, 2))
)
colnames(rbdf) <- c("Construct",
                    "Original model value",
                    "Original model p",
                    "DI copula model value",
                    "DI copula model p",
                    "KN copula model value",
                    "KN copula model p",
                    "DI & KN copula model value",
                    "DI & KN copula model p"
                    )
```

```{r gca rb table, echo = FALSE}
rbdft <- rbdf[,-1] %>% t() %>% as.data.frame()
colnames(rbdft) <- rbdf[,1]
rbdft %>% 
  datatable(caption = 'Results of the copula procedure for the regression of Response Beliefs') %>%
  formatRound(1:ncol(rbdft),
              digits = 3)
```


The Distrusting Beliefs copula is not significant, indicating that there is no endogeneity in the regression of Response Beliefs on its predictors.

# Regression of Threat Beliefs on Distrusting Beliefs and Knowledge

```{r gca tb, echo = FALSE, include = FALSE}
# Define Variables for easy access
KN <- model$construct_scores[,"Knowledge"]
TB <- model$construct_scores[,"Threat Beliefs"]

# Define number of bootstraps: 10.000 for reporting, 100 for testing
bootrounds <- 10000

# Estimate regression model
tbmodel <- lm(TB ~ DI + KN)
summary(tbmodel)
boottb <- Boot(tbmodel, R=bootrounds)
summary(boottb)

# Make base df
tbdf <- data.frame(Construct = c("Distrusting Beliefs", "Knowledge", "Copula Distrusting Beliefs", "Copula Knowledge"), 
                   Original.Model.Value = c(summary(bootrb)[2:3,5],NA,NA),
                   Original.Model.p = c(bootSig(model$data, bootrb, 2, 0)[2:3],NA,NA)
)

# Calculate copulas for independent variables - already happened
# KN_star <- createCopula(KN)
# DI_star <- createCopula(DI)


# Calculate results with copula for Distrusting Beliefs
# Input is regular model + copula + 0
copuladitb <- lm(TB ~ DI + KN + DI_star + 0)
summary(copuladitb)
# Bootstrap Standard Errors
bootcopuladitb <- Boot(copuladitb, R=bootrounds)
summary(bootcopuladitb)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopuladitb, 2,1)
# Attach to df
tbdf <- tbdf %>% cbind(
  DI.Co.Model.Value = c(summary(bootcopuladitb)[1:3,5], NA),
  DI.Co.Model.p = c(bootSig(model$data, bootcopuladitb, 2,1), NA)
)

# Calculate results with copula for Knowledge
# Input is regular model + copula + 0
copulakntb <- lm(TB ~ DI + KN + KN_star + 0)
summary(copulakntb)
# Bootstrap Standard Errors
bootcopulakntb <- Boot(copulakntb, R=bootrounds)
summary(bootcopulakntb)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopulakntb, 2,1)
# Attach to df
tbdf <- tbdf %>% cbind(
  KN.Co.Model.Value = c(summary(bootcopulakntb)[1:2,5], NA, summary(bootcopulakntb)[3,5]),
  KN.Co.Model.p = c(bootSig(model$data, bootcopuladitb, 2,1)[1:2], NA, bootSig(model$data, bootcopuladitb, 3,1)[3])
)

# Calculate results with copula for both DI and KN
# Input is regular model + copula + 0
copuladikntb <- lm(TB ~ DI + KN + DI_star + KN_star + 0)
summary(copuladikntb)
# Bootstrap Standard Errors
bootcopuladikntb <- Boot(copuladikntb, R=bootrounds)
summary(bootcopuladikntb)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootstrappedSignificance(model$data, bootcopuladikntb, 2, 2)
# Attach to df
tbdf <- tbdf %>% cbind(
  DIKN.Co.Model.Value = c(summary(bootcopuladikntb)[1:4,5]),
  DIKN.Co.Model.p = c(bootSig(model$data, bootcopuladikntb, 2, 2))
)
colnames(tbdf) <- c("Construct",
                    "Original model value",
                    "Original model p",
                    "DI copula model value",
                    "DI copula model p",
                    "KN copula model value",
                    "KN copula model p",
                    "DI & KN copula model value",
                    "DI & KN copula model p"
                    )


```
```{r gca tb table, echo = FALSE}
tbdft <- tbdf[,-1] %>% t() %>% as.data.frame()
colnames(tbdft) <- tbdf[,1]
tbdft %>% 
  datatable(caption = 'Results of the copula procedure for the regression of Threat Beliefs') %>%
  formatRound(1:ncol(tbdft),
              digits = 3)
```


Neither the Distrusting Beliefs nor the Knowledge Copula is significant, indicating that there is no endogeneity in the regression of Threat Beliefs on its predictors.

# Regression of Behavioral Intention on its predictors

```{r gca bi, echo = FALSE, include = FALSE}
# Define Variables for easy access
BI <- model$construct_scores[,"Behavioral Intention"]
PN <- model$construct_scores[,"Personal Moral Norm"]
DN <- model$construct_scores[,"Descriptive Norm"]

# Define number of bootstraps: 10.000 for reporting, 100 for testing
bootrounds <- 10000

# Estimate regression model
bimodel <- lm(BI ~ RB + TB + PN + DN)
summary(bimodel)
bootbi <- Boot(bimodel, R=bootrounds)
summary(bootbi)

# Make base df
bidf <- data.frame(Construct = c("Response Beliefs", "Threat Beliefs", "Personal Moral Norm", "Descriptive Norm", "Copula Response Beliefs", "Copula Threat Beliefs", "Copula Personal Moral Norm", "Copula Descriptive Norm"), 
                   Original.Model.Value = c(summary(bootbi)[2:5,5],NA,NA,NA,NA),
                   Original.Model.p = c(bootSig(model$data, bootbi, 4, 0)[2:5],NA,NA,NA,NA)
)

# Calculate copulas for independent variables - already happened
RB_star <- createCopula(RB)
TB_star <- createCopula(TB)
PN_star <- createCopula(PN)
DN_star <- createCopula(DN)

# Calculate results with copula for Response Beliefs
# Input is regular model + copula + 0
copularbbi <- lm(BI ~ RB + TB + PN + DN + RB_star + 0)
summary(copularbbi)
# Bootstrap Standard Errors
bootcopularbbi <- Boot(copularbbi)
summary(bootcopularbbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopularbbi, 4,1)
# Attach to df
bidf <- bidf %>% cbind(
  RB.Co.Model.Value = c(summary(bootcopularbbi)[,5], NA, NA, NA),
  RB.Co.Model.p = c(bootSig(model$data, bootcopularbbi, 4,1), NA, NA, NA)
)

# Calculate results with copula for Threat Beliefs
# Input is regular model + copula + 0
copulatbbi <- lm(BI ~ RB + TB + PN + DN + TB_star + 0)
summary(copulatbbi)
# Bootstrap Standard Errors
bootcopulatbbi <- Boot(copulatbbi)
summary(bootcopulatbbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopulatbbi, 4,1)
# Attach to df
bidf <- bidf %>% cbind(
  TB.Co.Model.Value = c(summary(bootcopulatbbi)[1:4,5], NA, summary(bootcopulatbbi)[5,5],  NA, NA),
  TB.Co.Model.p = c(bootSig(model$data, bootcopulatbbi, 4,1)[1:4], NA, bootSig(model$data, bootcopulatbbi, 4,1)[5], NA, NA)
)

# Calculate results with copula for Personal Moral Norm
# Input is regular model + copula + 0
copulapnbi <- lm(BI ~ RB + TB + PN + DN + PN_star + 0)
summary(copulapnbi)
# Bootstrap Standard Errors
bootcopulapnbi <- Boot(copulapnbi)
summary(bootcopulapnbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopulapnbi, 4,1)
# Attach to df
bidf <- bidf %>% cbind(
  PN.Co.Model.Value = c(summary(bootcopulapnbi)[1:4,5], NA, NA, summary(bootcopulapnbi)[5,5],  NA),
  PN.Co.Model.p = c(bootSig(model$data, bootcopulapnbi, 4,1)[1:4], NA,  NA, bootSig(model$data, bootcopulapnbi, 4,1)[5],NA)
)

# Calculate results with copula for Descriptive Norm
# Input is regular model + copula + 0
copulasnbi <- lm(BI ~ RB + TB + PN + DN + DN_star + 0)
summary(copulasnbi)
# Bootstrap Standard Errors
bootcopulasnbi <- Boot(copulasnbi)
summary(bootcopulasnbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopulasnbi, 4,1)
# Attach to df
bidf <- bidf %>% cbind(
  SN.Co.Model.Value = c(summary(bootcopulasnbi)[1:4,5], NA, NA, NA, summary(bootcopulasnbi)[5,5]),
  SN.Co.Model.p = c(bootSig(model$data, bootcopulasnbi, 4,1)[1:4], NA,  NA, NA, bootSig(model$data, bootcopulasnbi, 4,1)[5])
)

# Calculate results with copula for Response Beliefs and Threat Beliefs
# Input is regular model + copula + 0
copularbtbbi <- lm(BI ~ RB + TB + PN + DN + RB_star + TB_star + 0)
summary(copularbtbbi)
# Bootstrap Standard Errors
bootcopularbtbbi <- Boot(copularbtbbi)
summary(bootcopularbtbbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopularbtbbi, 4,2)
# Attach to df
bidf <- bidf %>% cbind(
  RB.TB.Co.Model.Value = c(summary(bootcopularbtbbi)[,5], NA, NA),
  RB.TB.Co.Model.p = c(bootSig(model$data, bootcopularbtbbi, 4,2), NA, NA)
)

# Calculate results with copula for Response Beliefs and Personal Moral Norm
# Input is regular model + copula + 0
copularbpnbi <- lm(BI ~ RB + TB + PN + DN + RB_star + PN_star + 0)
summary(copularbpnbi)
# Bootstrap Standard Errors
bootcopularbpnbi <- Boot(copularbpnbi)
summary(bootcopularbpnbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopularbpnbi, 4,2)
# Attach to df
bidf <- bidf %>% cbind(
  RB.PN.Co.Model.Value = c(summary(bootcopularbpnbi)[1:5,5], NA, summary(bootcopularbpnbi)[6,5], NA),
  RB.PN.Co.Model.p = c(bootSig(model$data, bootcopularbpnbi, 4,2)[1:5], NA, bootSig(model$data, bootcopularbpnbi, 4,2)[6], NA)
)

# Calculate results with copula for Response Beliefs and Descriptive Norm
# Input is regular model + copula + 0
copularbsnbi <- lm(BI ~ RB + TB + PN + DN + RB_star + DN_star + 0)
summary(copularbsnbi)
# Bootstrap Standard Errors
bootcopularbsnbi <- Boot(copularbsnbi)
summary(bootcopularbsnbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopularbsnbi, 4,2)
# Attach to df
bidf <- bidf %>% cbind(
  RB.SN.Co.Model.Value = c(summary(bootcopularbsnbi)[1:5,5], NA, NA, summary(bootcopularbsnbi)[6,5]),
  RB.SN.Co.Model.p = c(bootSig(model$data, bootcopularbsnbi, 4,2)[1:5], NA, NA, bootSig(model$data, bootcopularbsnbi, 4,2)[6])
)

# Calculate results with copula for Threat Beliefs and Personal Moral Norm
# Input is regular model + copula + 0
copulatbpnbi <- lm(BI ~ RB + TB + PN + DN + TB_star + PN_star + 0)
summary(copulatbpnbi)
# Bootstrap Standard Errors
bootcopulatbpnbi <- Boot(copulatbpnbi)
summary(bootcopulatbpnbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopulatbpnbi, 4,2)
# Attach to df
bidf <- bidf %>% cbind(
  TB.PN.Co.Model.Value = c(summary(bootcopulatbpnbi)[1:4,5], NA, summary(bootcopulatbpnbi)[5:6,5], NA),
  TB.PN.Co.Model.p = c(bootSig(model$data, bootcopulatbpnbi, 4,2)[1:4], NA, bootSig(model$data, bootcopulatbpnbi, 4,2)[5:6], NA)
)

# Calculate results with copula for Threat Beliefs and Descriptive Norm
# Input is regular model + copula + 0
copulatbsnbi <- lm(BI ~ RB + TB + PN + DN + TB_star + DN_star + 0)
summary(copulatbsnbi)
# Bootstrap Standard Errors
bootcopulatbsnbi <- Boot(copulatbsnbi)
summary(bootcopulatbsnbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopulatbsnbi, 4,2)
# Attach to df
bidf <- bidf %>% cbind(
  TB.SN.Co.Model.Value = c(summary(bootcopulatbsnbi)[1:4,5], NA, summary(bootcopulatbsnbi)[5,5], NA, summary(bootcopulatbsnbi)[6,5]),
  TB.SN.Co.Model.p = c(bootSig(model$data, bootcopulatbsnbi, 4,2)[1:4], NA, bootSig(model$data, bootcopulatbsnbi, 4,2)[6], NA, bootSig(model$data, bootcopulatbsnbi, 4,2)[6])
)

# Calculate results with copula for Personal Moral Norm and Descriptive Norm
# Input is regular model + copula + 0
copulapnsnbi <- lm(BI ~ RB + TB + PN + DN + PN_star + DN_star + 0)
summary(copulapnsnbi)
# Bootstrap Standard Errors
bootcopulapnsnbi <- Boot(copulapnsnbi)
summary(bootcopulapnsnbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopulapnsnbi, 4,2)
# Attach to df
bidf <- bidf %>% cbind(
  PN.SN.Co.Model.Value = c(summary(bootcopulapnsnbi)[1:4,5], NA, NA, summary(bootcopulapnsnbi)[5:6,5]),
  PN.SN.Co.Model.p = c(bootSig(model$data, bootcopulapnsnbi, 4,2)[1:4], NA, NA, bootSig(model$data, bootcopulapnsnbi, 4,2)[5:6])
)

# Calculate results with copula for Response Beliefs, Threat Beliefs and Personal Moral Norm
# Input is regular model + copula + 0
copularbtbpnbi <- lm(BI ~ RB + TB + PN + DN + RB_star + TB_star + PN_star + 0)
summary(copularbtbpnbi)
# Bootstrap Standard Errors
bootcopularbtbpnbi <- Boot(copularbtbpnbi)
summary(bootcopularbtbpnbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopularbtbpnbi, 4,3)
# Attach to df
bidf <- bidf %>% cbind(
  RB.TB.PN.Co.Model.Value = c(summary(bootcopularbtbpnbi)[,5], NA),
  RB.TB.PN.Co.Model.p = c(bootSig(model$data, bootcopularbtbpnbi, 4,3), NA)
)

# Calculate results with copula for Response Beliefs, Threat Beliefs and Descriptive Norm
# Input is regular model + copula + 0
copularbtbsnbi <- lm(BI ~ RB + TB + PN + DN + RB_star + TB_star + DN_star + 0)
summary(copularbtbsnbi)
# Bootstrap Standard Errors
bootcopularbtbsnbi <- Boot(copularbtbsnbi)
summary(bootcopularbtbsnbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopularbtbsnbi, 4,3)
# Attach to df
bidf <- bidf %>% cbind(
  RB.TB.SN.Co.Model.Value = c(summary(bootcopularbtbsnbi)[1:6,5], NA, summary(bootcopularbtbsnbi)[7,5]),
  RB.TB.SN.Co.Model.p = c(bootSig(model$data, bootcopularbtbsnbi, 4,3)[1:6], NA, bootSig(model$data, bootcopularbtbsnbi, 4,3)[7])
)

# Calculate results with copula for Response Beliefs, Personal Moral Norm and Descriptive Norm
# Input is regular model + copula + 0
copularbpnsnbi <- lm(BI ~ RB + TB + PN + DN + RB_star + PN_star + DN_star + 0)
summary(copularbpnsnbi)
# Bootstrap Standard Errors
bootcopularbpnsnbi <- Boot(copularbpnsnbi)
summary(bootcopularbpnsnbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopularbpnsnbi, 4,3)
# Attach to df
bidf <- bidf %>% cbind(
  RB.PN.SN.Co.Model.Value = c(summary(bootcopularbpnsnbi)[1:5,5], NA, summary(bootcopularbpnsnbi)[6:7,5]),
  RB.PN.SN.Co.Model.p = c(bootSig(model$data, bootcopularbpnsnbi, 4,3)[1:5], NA, bootSig(model$data, bootcopularbpnsnbi, 4,3)[6:7])
)

# Calculate results with copula for Threat Beliefs, Personal Moral Norm and Descriptive Norm
# Input is regular model + copula + 0
copulatbpnsnbi <- lm(BI ~ RB + TB + PN + DN + TB_star + PN_star + DN_star + 0)
summary(copulatbpnsnbi)
# Bootstrap Standard Errors
bootcopulatbpnsnbi <- Boot(copulatbpnsnbi)
summary(bootcopulatbpnsnbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopulatbpnsnbi, 4,3)
# Attach to df
bidf <- bidf %>% cbind(
  TB.PN.SN.Co.Model.Value = c(summary(bootcopulatbpnsnbi)[1:4,5], NA, summary(bootcopulatbpnsnbi)[5:7,5]),
  TB.PN.SN.Co.Model.p = c(bootSig(model$data, bootcopulatbpnsnbi, 4,3)[1:4], NA, bootSig(model$data, bootcopulatbpnsnbi, 4,3)[5:7])
)

# Calculate results with copula for Response Beliefs, Threat Beliefs, Personal Moral Norm and Descriptive Norm
# Input is regular model + copula + 0
copularbtbpnsnbi <- lm(BI ~ RB + TB + PN + DN + RB_star + TB_star + PN_star + DN_star + 0)
summary(copularbtbpnsnbi)
# Bootstrap Standard Errors
bootcopularbtbpnsnbi <- Boot(copularbtbpnsnbi)
summary(bootcopularbtbpnsnbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopularbtbpnsnbi, 4,4)
# Attach to df
bidf <- bidf %>% cbind(
  RB.TB.PN.SN.Co.Model.Value = c(summary(bootcopularbtbpnsnbi)[,5]),
  RB.TB.PN.SN.Co.Model.p = c(bootSig(model$data, bootcopularbtbpnsnbi, 4,4))
)
colnames(bidf) <- c("Construct",
                    "Original model value",
                    "Original model p",
                    "RB copula model value",
                    "RB copula model p",
                    "TB copula model value",
                    "TB copula model p",
                    "PN copula model value",
                    "PN copula model p",
                    "DN copula model value",
                    "DN copula model p",
                    "RB & TB copula model value",
                    "RB & TB copula model p",
                    "RB & PN copula model value",
                    "RB & PN copula model p",
                    "RB & DN copula model value",
                    "RB & DN copula model p",
                    "TB & PN copula model value",
                    "TB & PN copula model p",
                    "TB & DN copula model value",
                    "TB & DN copula model p",
                    "PN & DN copula model value",
                    "PN & DN copula model p",
                    "RB & TB & PN copula model value",
                    "RB & TB & PN copula model p",
                    "RB & TB & DN copula model value",
                    "RB & TB & DN copula model p",
                    "RB & PN & DN copula model value",
                    "RB & PN & DN copula model p",
                    "TB & PN & DN copula model value",
                    "TB & PN & DN copula model p",
                    "RB & TB & PN & DN copula model value",
                    "RB & TB & PN & DN copula model p"
                    )

```
```{r gca bi table, echo = FALSE, layout = "l-page"}
bidft <- bidf[,-1] %>% t() %>% as.data.frame()
colnames(bidft) <- bidf[,1]
bidft %>% 
  datatable(caption = 'Results of the copula procedure for the regression of Behavioral Intention') %>%
  formatRound(1:ncol(bidft),
              digits = 3)
```

The copula for Descriptive Norm achieves a significant p-value (p < 0.1) both in the model with only the Descriptive Norm copula and in combination with other copulas.
However, the addition of the copula leads to the path coefficient of Descriptive Norm being inverted.
In terms of interpretation, that would imply that Descriptive Norm has a negative influence on Behavioral Intention, which is not theoretically grounded.
Other than that, there is a significant copula  for Threat Beliefs in the model with the Descriptive Norm copula.
As the inclusion does not lead to a substantial increase of the path coefficient, this can likely be disregarded.
There is nothing pointing to endogeneity in any of the other predictors.

As the copula cannot be integrated in iterative model improvement, the copula test will be repeated for the final models.
