---
title: "Climate Crisis Iteration 2-b-2 (Heating) Nonlinearity Evaluation"
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
---

```{r setup, echo =FALSE, include=FALSE}
# Include libraries
library(tidyverse)
library(seminr)
library(DT)
library(htmltools)
library(lmtest)
library(distill)
library(targets)
source(here::here("R", "02_sem-evaluation.R"))
# Load models
tar_config_set(here::here("_targets"))
model <- tar_read("cc_model_2_b_2")
bootmodel <- tar_read("cc_model_2_b_2_boot")
proxymodel <- tar_read("cc_model_2_b_2_proxy")
bootprmodel <- tar_read("cc_model_2_b_2_proxy_boot")
# Make summaries
summo <- summary(model)
sumbomo <- summary(bootmodel)
sumprmo <- summary(proxymodel)
sumboprmo <- summary(bootprmodel)
```

# Test for possible nonlinearity

First, we test for nonlinearity by applying Ramsey's RESET test for functional form to each partial linear model of the SEM.
As quadratic effects of higher-order constructs cannot (yet) be estimated using PLS-SEM, we also apply the test to the corresponding partial linear models of the proxy SEM without higher order constructs.
If the test statistic is significant, the respective partial regression might be nonlinear.

```{r reset, echo = FALSE}
# Make df with independent and response variable
varlist <- as_tibble(model$smMatrix)
# Make df
resetdf <- data.frame(
  'Independent variable' = character(),
  'Response variable' = character(),
  'Test statistic' = double(),
  'p' = double(),
  'DF 1' = double(),
  'DF 2' = double()
)
# Fill df
for (i in 1:nrow(varlist)) {
  resetdf <- resetdf %>% rbind(resetfun(varlist[[i, 1]],
                                        varlist[[i, 2]]))
}
resetdf %>%
  datatable(
    rownames = FALSE,
    caption = 'Results of Ramsey\'s RESET test for nonlinearity') %>%
  formatRound(c(3:4),
              3)
```
Using p = 0.05 as a threshold, there are potential nonlinear effects in the partial regression equation for the influence of Knowledge on Response Beliefs.
The same is potentially true for the effects of Distrusting Beliefs and Knowledge on Threat Beliefs.
But as Threat Beliefs itself has to be removed from the model due to a lack of effect on Behavioral intention, only the effect of Knoweldge on Response Beliefs will be evaluated.

# Test alternate models with quadratic effects
To test for nonlinearity, one can model an interaction term of the exogenous construct with itself.

## Effect of Knowledge on Response Beliefs
```{r rb alt nonlinear estimate, echo = FALSE, include = FALSE}
# Estimate alternate model with quadratic effect - HOCs as proxy
morbalt <- estimate_pls(
  data = model$data %>% as.data.frame(),
  measurement_model = constructs(
    composite("Response Beliefs", multi_items("CCRB", c(2,5)), weights = mode_B),
    composite("Distrusting Beliefs", multi_items("CCDI", 1:9), weights = mode_B),
    composite("Knowledge1", single_item("CCKN")),
    composite("Knowledge2", single_item("CCKN")),
    interaction_term("Knowledge1", "Knowledge2", method = orthogonal),
    composite("Threat Beliefs", multi_items("CCTB", 1:6)),
    composite("Subjective Norm", c(multi_items("CCDN", 1:2), multi_items("CCIN",1:2))),
    composite("Personal Moral Norm", multi_items("CCPN", c(1,3))),
    composite("Behavioral Intention", single_item("CCBI1"))
  ),
  structural_model = relationships(
    paths(
      from = c("Distrusting Beliefs", "Knowledge1"),
      to = c("Threat Beliefs")
    ),
    paths(
    from = c("Distrusting Beliefs", "Knowledge1*Knowledge2"),
    to = c("Response Beliefs")
    ),
    paths(
      from = c(
        "Response Beliefs",
        "Threat Beliefs",
        "Personal Moral Norm",
        "Subjective Norm"
      ),
      to = "Behavioral Intention"
    )
  )
)
# Estimate second model for f2 with construct excluded
morbaltex <- estimate_pls(
  data = model$data,
  measurement_model = constructs(
    composite("Response Beliefs", multi_items("CCRB", c(2,5)), weights = mode_B),
    composite("Benevolence", multi_items("CCDI", 1:3)),
    composite("Competence", multi_items("CCDI", 4:6)),
    composite("Integrity", multi_items("CCDI", 7:9)),
    higher_composite("Distrusting Beliefs", c("Benevolence", "Competence", "Integrity"), weights = mode_B),
    composite("Perceived Susceptibility", multi_items("CCTB", 1:3)),
    composite("Perceived Severity", multi_items("CCTB", 4:6)),
    higher_composite("Threat Beliefs", c("Perceived Susceptibility", "Perceived Severity"), weights = mode_B),
    composite("Personal Moral Norm", multi_items("CCPN",c(1,3))),
    composite("Descriptive Norm", multi_items("CCDN", 1:2), mode_B),
    composite("Injunctive Norm", multi_items("CCIN", 1:2), mode_B),
    higher_composite("Subjective Norm", c("Descriptive Norm", "Injunctive Norm"), weights = mode_B),
    composite("Behavioral Intention", single_item("CCBI1"))
  ),
  structural_model = relationships(
    paths(from = c("Distrusting Beliefs"), to = c("Threat Beliefs", "Response Beliefs")),
    paths(from = c("Threat Beliefs", "Response Beliefs", "Personal Moral Norm", "Subjective Norm"), to = "Behavioral Intention")
  )
)
# Bootstrap model for significance (500 samples)
sumbomorbalt <- morbalt %>%
  bootstrap_model() %>%
  summary()
```
```{r bi1 alt results, echo = FALSE}
# Print datatable
nldfdt("Knowledge",
     "Response Beliefs",
     morbalt,
     morbaltex,
     sumbomorbalt)
```

For the alternate model, Knowledge is specified as a quadratic influence.
Although the correct method would be two-stage, only the orthogonal method worked.
Using this method, the effect size is just above the 0.02 threshold, but the t-statistic does not indicate significance.
This points to a linear effect of Knowledge on Response Beliefs.


# Summary
Using the available tests, we did not find evidence for a quadratic influence of any of the exogenous variables.
