---
title: "Climate Crisis Iteration 2-d-2 (General) Structural Model Evaluation"
output: 
  distill::distill_article:
    toc: true
    toc_depth: 1
---

```{r setup, echo =FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Include libraries
library(tidyverse)
library(seminr)
library(DT)
library(htmltools)
library(targets)
source(here::here("R", "02_sem-evaluation.R"))
# Load models
tar_config_set(here::here("_targets"))
model <- tar_read("cc_model_2_d_2")
bootmodel <- tar_read("cc_model_2_d_2_boot")
sumplspre <- tar_read("cc_model_2_d_2_plspre")
# Make summaries
# model summary throws error
# summo <- summary(model)
sumbomo <- summary(bootmodel)
# Set seminr plot theme
thm <-
  seminr_theme_create(
    construct.compositeA.arrow = "backward",
    construct.compositeA.use_weights = FALSE,
    plot.adj = FALSE
  )
seminr_theme_set(thm)
# My favorite operator
`%notin%` <- Negate(`%in%`)
```

# Model plots

## Structural Model Only

This is a path model showing only the structural model components.

```{r plot mm model, echo=FALSE}
plot(bootmodel, structure_only = TRUE)
```

# Collinearity

Collinearity is assessed using the variance inflation factor (VIF). VIF should be < 5, ideally $\leq$ 3.

```{r collinearity vif, echo = FALSE}
modelval <- validity(model)
vif <- data.frame('Exogenous Construct' = character(),
                  'Endogenous Construct' = character(),
                  VIF = double ())
for (i in 1:length(modelval$antecedent_vifs)){
  x = names(modelval$antecedent_vifs[i])
  for (j in 1:length(modelval$antecedent_vifs[[{{x}}]])){
    y = names(modelval$antecedent_vifs[[{{x}}]])[j]
    vif <- vif %>% rbind(data.frame('Exogenous Construct' = {{y}},
                                    'Endogenous Construct' = {{x}},
                                    VIF = modelval$antecedent_vifs[[{{x}}]][j]))
    }
  }
vif %>%
  datatable(
          filter = 'top',
          options = list(pageLength = nrow(vif)),
          rownames = FALSE,
          colnames = c('Exogenous Construct' = 1,
                        'Endogenous Construct' = 2),
          caption = 'Results of the structural collinearity assessment') %>%
  formatRound(3,
              digits = 3) %>%
  formatStyle('VIF', backgroundColor = styleInterval(cuts = c(3,5), values = c('#00', '#ffe5e5','#ff9999')))
```
There is no VIF information for the path from Distrusting Beliefs to Response Beliefs, as Distrusting Beliefs is the only predictor.
Other than that, all VIF values are below 3.

# In-sample predictive power

In-sample predictive power is assessed using variance explained R². R² $\geq$ 0.75 indicates substantial in-sample predictive power, R² $\geq$ 0.5 moderate and R² $\geq$ 0.25 weak in-sample predictive power. R² $\leq$ 0.10 indicates a lack of model predictiveness.

```{r in-sample pp r^2, echo=FALSE}
r2 <- data.frame(Construct = colnames(model$rSquared),
                      "R^2" = model$rSquared[1,],
                      "AdjR^2" = model$rSquared[2,])
r2 %>% 
  datatable(
    filter = 'top',
    options = list(pageLength = nrow(r2)),
    rownames = FALSE,
    colnames = c('R²' = 2,
                  'R²adj' = 3),
    caption = 'In-sample predictive power') %>%
  formatRound(2:3,
              digits = 3) %>%
  formatStyle('R²', backgroundColor = styleInterval(cuts = c(0.1,0.249,0.9), values = c('#ff9999', '#ffe5e5', '#00','#ff9999')))
```

All R² values are above 0.25, indicating weak in-sample predictive power at a minimum.

# Effect size

Effect size f2² measures the impact of a predictor construct on an endogenous construct. f² $\geq$ 0.35 indicates a large effect, f² $\geq$ 0.15 a medium and f² $\geq$ 0.02 a small effect.

```{r effect size f^2, echo=FALSE}
# f2 cannot be calculated automatically for this model 
# in fact, it is why the summary function fails
# manual calculation
# f2 = (r2included - r2excluded)/(1-r2included)
modelnorb <- estimate_pls(
  data = model$data, 
  measurement_model = constructs(
    composite("Personal Moral Norm", multi_items("CCPN",c(1,3))),
    composite("Descriptive Norm", multi_items("CCDN", 1:2), mode_B),
    composite("Injunctive Norm", multi_items("CCIN", 1:2), mode_B),
    higher_composite("Subjective Norm", c("Descriptive Norm", "Injunctive Norm"), weights = mode_B),
    composite("Behavioral Intention", single_item("CCBI4"))
  ),
  structural_model = relationships(
    paths(from = c("Personal Moral Norm", "Subjective Norm"), to = "Behavioral Intention")
  )
)
modelnopn <- estimate_pls(
  data = model$data, 
  measurement_model = constructs(
    composite("Perceived Self-Efficacy", single_item("CCRB10")),
    composite("Perceived Response Efficacy", single_item("CCRB11")),
    composite("Perceived Response Costs", single_item("CCRB12")),
    higher_composite("Response Beliefs", c("Perceived Self-Efficacy", "Perceived Response Efficacy", "Perceived Response Costs"), weights = mode_B),
    composite("Benevolence", multi_items("CCDI", 1:3)),
    composite("Competence", multi_items("CCDI", 4:6)),
    composite("Integrity", multi_items("CCDI", 7:9)),
    higher_composite("Distrusting Beliefs", c("Benevolence", "Competence", "Integrity"), weights = mode_B),
    composite("Descriptive Norm", multi_items("CCDN", 1:2), mode_B),
    composite("Injunctive Norm", multi_items("CCIN", 1:2), mode_B),
    higher_composite("Subjective Norm", c("Descriptive Norm", "Injunctive Norm"), weights = mode_B),
    composite("Behavioral Intention", single_item("CCBI4"))
  ),
  structural_model = relationships(
    paths(from = "Distrusting Beliefs", to = "Response Beliefs"),
    paths(from = c("Response Beliefs", "Subjective Norm"), to = "Behavioral Intention")
  )
)
modelnosn <- estimate_pls(
  data = model$data, 
  measurement_model = constructs(
    composite("Perceived Self-Efficacy", single_item("CCRB10")),
    composite("Perceived Response Efficacy", single_item("CCRB11")),
    composite("Perceived Response Costs", single_item("CCRB12")),
    higher_composite("Response Beliefs", c("Perceived Self-Efficacy", "Perceived Response Efficacy", "Perceived Response Costs"), weights = mode_B),
    composite("Benevolence", multi_items("CCDI", 1:3)),
    composite("Competence", multi_items("CCDI", 4:6)),
    composite("Integrity", multi_items("CCDI", 7:9)),
    higher_composite("Distrusting Beliefs", c("Benevolence", "Competence", "Integrity"), weights = mode_B),
    composite("Personal Moral Norm", multi_items("CCPN",c(1,3))),
    composite("Behavioral Intention", single_item("CCBI4"))
  ),
  structural_model = relationships(
    paths(from = "Distrusting Beliefs", to = "Response Beliefs"),
    paths(from = c("Response Beliefs", "Personal Moral Norm"), to = "Behavioral Intention")
  )
)
f2vec <- c(
  (model$rSquared[1,1] - 0)/(1-model$rSquared[1,1]),
  (model$rSquared[1,2] - modelnorb$rSquared[1,1])/(1-model$rSquared[1,2]),
  (model$rSquared[1,2] - modelnopn$rSquared[1,2])/(1-model$rSquared[1,2]),
  (model$rSquared[1,2] - modelnosn$rSquared[1,2])/(1-model$rSquared[1,2])
  )
f2 <- data.frame("Exogenous Construct" = vif[,1],
                 "Endogenous Construct" = vif[,2],
                 f2 = f2vec)
f2 %>%
  datatable(
          filter = 'top',
          rownames = FALSE,
          colnames = c('f²' = 3),
          caption = 'Effect sizes') %>%
  formatRound(3,
              digits = 3) %>%
  formatStyle('f²', backgroundColor = styleInterval(cuts = c(0.019), values = c('#ff9999', '#00')))
```
All effects are small at a minimum.

# Out-of-sample predictive performance

Out-of-sample predictive performance has to be evaluated using a simplified model without HOCs as an approximation as seminr as of now does not support plspredict for HOC.
If the root mean square error (RMSE) or the mean absolute deviation (MAD) of the naive LM model is below the ones for the PLS model, this indicates a lack of predictive performance.
However, a lack of predictive performance does not imply a lack of explanatory power.

```{r plspredict, echo = FALSE, layout="l-page"}
oospp <- (as.data.frame(sumplspre$PLS_out_of_sample) %>%
  rbind(as.data.frame(sumplspre$LM_out_of_sample)) %>%
  rbind((as.data.frame(sumplspre$LM_out_of_sample))[1,] - (as.data.frame(sumplspre$PLS_out_of_sample))[1,]) %>%
  rbind((as.data.frame(sumplspre$LM_out_of_sample))[2,] - (as.data.frame(sumplspre$PLS_out_of_sample))[2,])  %>%
  cbind(`Prediction Errors` = c("PLS RMSE", "PLS MAD", "LM RMSE", "LM MAD", "RMSE Difference", "MAD Difference")))[c(1,3,5,2,4,6),c(ncol(sumplspre$PLS_out_of_sample)+1,1:ncol(sumplspre$PLS_out_of_sample))]
datatable(oospp,
          options = list(pageLength = nrow(oospp)),
          rownames = FALSE,
          caption = 'Out-of-sample predictive performance') %>%
  formatRound(-1,
              digits = 3) %>%
  formatStyle(names(oospp), backgroundColor = styleInterval(cuts = c(0), values = c('#ff9999', '#00')))
```

Only CCBI4 is predicted better by the model than the LM in terms of both RMSE and MAD.
This indicates low predictive power.

# Significance and relevance of path coefficients

Significance is denoted by t-test and p values. A t of $\geq$ 1.65 signifies significance at the 10 % level, t $\geq$ 1.96 at the 5 % level and t $\geq$ 2.57 at the 1 % level.

```{r path-coeff, echo = FALSE, layout="l-page"}
pcdf <- make_pc_table(sumbomo)
datatable(pcdf,
          filter = 'top',
          rownames = FALSE,
          colnames = c("Original Estimate" = 3),
          caption = 'Relevance and significance of path coefficients') %>%
  formatRound(c(3:7, 9:10),
              digits = 3) %>%
  formatStyle(colnames(pcdf)[9], backgroundColor = styleInterval(cuts = c(1.649), values = c('#ff9999', '#00'))) %>%
  formatStyle('p', backgroundColor = styleInterval(cuts = c(0.049), values = c( '#00', '#ff9999'))) %>%
  formatStyle('0 in CI', backgroundColor = styleEqual(c(1,0), c('#ff9999', '#00'), default = NULL))
```

All path coefficients are significant and relevant.

# Summary table

```{r summary table-df print, echo = FALSE, layout="l-page"}
sumsm <- pcdf[,-c(5:7)] %>%
    left_join(f2 %>% rename('Exogenous Construct' = 'Exogenous.Construct',
                            'Endogenous Construct' = 'Endogenous.Construct'))  %>%
    left_join(vif %>% rename('Exogenous Construct' = 'Exogenous.Construct',
                             'Endogenous Construct' = 'Endogenous.Construct')) %>%
    rename('Path Coefficient Bootstrap Mean' = 'Bootstrap Mean',
           '0 in Path Coefficient CI' = '0 in CI',
           'Path Coefficient p' = 'p',
           'Path Coefficient Original Estimate' = 'Original Est.')
colnames(sumsm)[6] <- paste0("Path Coefficient t(", nrow(model$data), ")")
datatable(sumsm,
          filter = 'top',
          options = list(pageLength = nrow(sumsm)),
          rownames = FALSE,
          colnames = c("f²" = 8),
          caption = 'Structural Model Summary') %>%
  formatRound(c(3:4,6:9),
              digits = 3) %>%
  formatStyle(colnames(sumsm)[6], backgroundColor = styleInterval(cuts = c(1.649), values = c('#ff9999', '#00'))) %>%
  formatStyle('Path Coefficient p', backgroundColor = styleInterval(cuts = c(0.049), values = c( '#00', '#ff9999'))) %>%
  formatStyle('0 in Path Coefficient CI', backgroundColor = styleEqual(c(1,0), c('#ff9999', '#00'), default = NULL)) %>%
  formatStyle('VIF', backgroundColor = styleInterval(cuts = c(3,5), values = c('#00', '#ffe5e5','#ff9999')))
```

# Results summary

All paths are substantial in terms of both the path coefficients and effect size.
Structural model evaluation for this model is completed.
As there have been no indications of nonlinearity in earlier model iterations, this is not tested again.

```{r table-getter, echo = FALSE, include = FALSE}
write_excel_csv(sumsm[,-5] %>% mutate(across(c(3:5,7:8),  round, 2)) %>% mutate(across(c(6),  round, 3)), "paper/smeval-cc-2-d-2.csv",delim = ";")
```
