---
title: "Climate Crisis Iteration 2-a-2 (Diet) Nonlinearity Evaluation"
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
---

```{r setup, echo =FALSE, include=FALSE}
# Include libraries
library(tidyverse)
library(seminr)
library(DT)
library(htmltools)
library(lmtest)
library(distill)
library(targets)
source(here::here("R", "02_sem-evaluation.R"))
# Load models
tar_config_set(here::here("_targets"))
model <- tar_read("cc_model_2_a_2")
bootmodel <- tar_read("cc_model_2_a_2_boot")
proxymodel <- tar_read("cc_model_2_a_2_proxy")
bootprmodel <- tar_read("cc_model_2_a_2_proxy_boot")
# Make summaries
summo <- summary(model)
sumbomo <- summary(bootmodel)
sumprmo <- summary(proxymodel)
sumboprmo <- summary(bootprmodel)
```

# Test for possible nonlinearity

First, we test for nonlinearity by applying Ramsey's RESET test for functional form to each partial linear model of the SEM.
As quadratic effects of higher-order constructs cannot (yet) be estimated using PLS-SEM, we also apply the test to the corresponding partial linear models of the proxy SEM without higher order constructs.
If the test statistic is significant, the respective partial regression might be nonlinear.

```{r reset, echo = FALSE}
# Make df with independent and response variable
varlist <- as_tibble(model$smMatrix)
# Make df
resetdf <- data.frame(
  'Independent variable' = character(),
  'Response variable' = character(),
  'Test statistic' = double(),
  'p' = double(),
  'DF 1' = double(),
  'DF 2' = double()
)
# Fill df
for (i in 1:nrow(varlist)) {
  resetdf <- resetdf %>% rbind(resetfun(varlist[[i, 1]],
                                        varlist[[i, 2]]))
}
resetdf %>%
  datatable(
    rownames = FALSE,
    caption = 'Results of Ramsey\'s RESET test for nonlinearity') %>%
  formatRound(c(3:4),
              3)
```
Using p = 0.05 as a threshold, there are potential nonlinear effects in the partial regression equation for the influence of Response Beliefs on Behavioral Intention.
The same is potentially true for the effects of Distrusting Beliefs and Knowledge on Threat Beliefs.

# Test alternate models with quadratic effects
To test for nonlinearity, one can model an interaction term of the exogenous construct with itself.

## Effect of Response Beliefs on Behavioral Intention
```{r bi1 alt nonlinear estimate, echo = FALSE, include = FALSE}
# Estimate alternate model with quadratic effect - HOCs as proxy
mobi1alt <- estimate_pls(
  data = model$data,
  measurement_model = constructs(
    composite("Response Beliefs 1", multi_items("CCRB", c(1,4)), weights = mode_B),
    composite("Response Beliefs 2", multi_items("CCRB", c(1,4)), weights = mode_B),
    interaction_term("Response Beliefs 1", "Response Beliefs 2", method = two_stage),
    composite("Distrusting Beliefs", multi_items("CCDI", 1:9), weights = mode_B),
    composite("Knowledge", single_item("CCKN")),
    composite("Threat Beliefs", multi_items("CCTB", 1:6)),
    composite("Subjective Norm", c(multi_items("CCDN", 1:2), multi_items("CCIN",1:2))),
    composite("Personal Moral Norm", multi_items("CCPN", c(1,3))),
    composite("Behavioral Intention", single_item("CCBI1"))
  ),
  structural_model = relationships(
    paths(
      from = c("Distrusting Beliefs", "Knowledge"),
      to = c("Response Beliefs 1",
              "Response Beliefs 2", 
             "Threat Beliefs")
    ),
    paths(
      from = c(
        "Response Beliefs 1*Response Beliefs 2",
        "Threat Beliefs",
        "Personal Moral Norm",
        "Subjective Norm"
      ),
      to = "Behavioral Intention"
    )
  )
)
# Estimate second model for f2 with construct excluded
mobi1altex <- estimate_pls(
  data = model$data,
  measurement_model = constructs(
    composite("Benevolence", multi_items("CCDI", 1:3)),
    composite("Competence", multi_items("CCDI", 4:6)),
    composite("Integrity", multi_items("CCDI", 7:9)),
    higher_composite("Distrusting Beliefs", c("Benevolence", "Competence", "Integrity"), weights = mode_B),
    composite("Knowledge", single_item("CCKN")),
    composite("Perceived Susceptibility", multi_items("CCTB", 1:3)),
    composite("Perceived Severity", multi_items("CCTB", 4:6)),
    higher_composite("Threat Beliefs", c("Perceived Susceptibility", "Perceived Severity"), weights = mode_B),
    composite("Personal Moral Norm", multi_items("CCPN",c(1,3))),
    composite("Descriptive Norm", multi_items("CCDN", 1:2), mode_B),
    composite("Injunctive Norm", multi_items("CCIN", 1:2), mode_B),
    higher_composite("Subjective Norm", c("Descriptive Norm", "Injunctive Norm"), weights = mode_B),
    composite("Behavioral Intention", single_item("CCBI1"))
  ),
  structural_model = relationships(
    paths(from = c("Distrusting Beliefs", "Knowledge"), to = c("Threat Beliefs")),
    paths(from = c("Threat Beliefs", "Personal Moral Norm", "Subjective Norm"), to = "Behavioral Intention")
  )
)
# Bootstrap model for significance (500 samples)
sumbomobi1alt <- mobi1alt %>%
  bootstrap_model() %>%
  summary()
```
```{r bi1 alt results, echo = FALSE}
# Print datatable
nldfdt("Response Beliefs",
     "Behavioral Intention",
     mobi1alt,
     mobi1altex,
     sumbomobi1alt)
```

For the alternate model with Response Beliefs as a quadratic influence, the effect size is negligible, as is the t-value.
This points to a linear effect of Response Beliefs on Behavioral Intention.

## Effect of Distrusting Beliefs on Threat Beliefs

<!-- ```{r tb1 alt nonlinear estimate, echo = F, include = F} -->
<!-- # Estimate alternate model with quadratic effect - HOCs as proxy -->
<!-- # motb1alt <- estimate_pls( -->
<!-- #   data = model$data, -->
<!-- #   measurement_model = constructs( -->
<!-- #     composite("Response Beliefs", multi_items("CCRB", c(1,4)), weights = mode_B), -->
<!-- #     composite("Distrusting Beliefs 1", multi_items("CCDI", 1:9), weights = mode_B), -->
<!-- #     composite("Distrusting Beliefs 2", multi_items("CCDI", 1:9), weights = mode_B), -->
<!-- #     interaction_term("Distrusting Beliefs 1", "Distrusting Beliefs 2", method = two_stage), -->
<!-- #     composite("Knowledge", single_item("CCKN")), -->
<!-- #     composite("Threat Beliefs", multi_items("CCTB", 1:6)), -->
<!-- #     composite("Subjective Norm", c(multi_items("CCDN", 1:2), multi_items("CCIN",1:2))), -->
<!-- #     composite("Personal Moral Norm", multi_items("CCPN", c(1,3))), -->
<!-- #     composite("Behavioral Intention", single_item("CCBI1")) -->
<!-- #   ), -->
<!-- #   structural_model = relationships( -->
<!-- #     paths( -->
<!-- #       from = c("Distrusting Beliefs 1", "Knowledge"), -->
<!-- #       to = c("Response Beliefs")), -->
<!-- #     paths( -->
<!-- #        from = c("Distrusting Beliefs 1*Distrusting Beliefs 2", "Knowledge"), -->
<!-- #       to = c("Response Beliefs", -->
<!-- #              "Threat Beliefs") -->
<!-- #  -->
<!-- #     ), -->
<!-- #     paths( -->
<!-- #       from = c( -->
<!-- #         "Response Beliefs", -->
<!-- #         "Threat Beliefs", -->
<!-- #         "Personal Moral Norm", -->
<!-- #         "Subjective Norm" -->
<!-- #       ), -->
<!-- #       to = "Behavioral Intention" -->
<!-- #     ) -->
<!-- #   ) -->
<!-- # ) -->
<!-- # Again, two-stage, though correct, does not work -> use ort and pi -->
<!-- motb1altort <- estimate_pls( -->
<!--   as.data.frame(model$data), -->
<!--   measurement_model = constructs( -->
<!--     composite("Response Beliefs", multi_items("CCRB", c(1,4)), weights = mode_B), -->
<!--     composite("DistrustingBeliefs1", multi_items("CODI", 1:9), weights = mode_B), -->
<!--     composite("DistrustingBeliefs2", multi_items("CODI", 1:9), weights = mode_B), -->
<!--     interaction_term("DistrustingBeliefs1", "DistrustingBeliefs2", method = orthogonal), -->
<!--     composite("Knowledge", single_item("COKN")), -->
<!--     composite("Threat Beliefs", multi_items("CCTB", 1:6)), -->
<!--     composite("Personal Moral Norm", multi_items("COPN", c(1,3))), -->
<!--     composite("Subjective Norm", c(multi_items("CCDN", 1:2), multi_items("CCIN",1:2))), -->
<!--     composite("Behavioral Intention", multi_items("COBI", 1:3), mode_B) -->
<!--     ), -->
<!--   structural_model = relationships( -->
<!--     paths(from = c("DistrustingBeliefs1*DistrustingBeliefs2", "Knowledge"), to = c("Threat Beliefs")), -->
<!--     paths(from = c("DistrustingBeliefs1", "Knowledge"), to = c("Response Beliefs")), -->
<!--     paths(from = c("Response Beliefs", "Threat Beliefs", "Personal Moral Norm", "Subjective Norm"), to = "Behavioral Intention") -->
<!--   ) -->
<!-- ) -->
<!-- motb1altpi <- estimate_pls( -->
<!--   as.data.frame(model$data), -->
<!--   measurement_model = constructs( -->
<!--     composite("Perceived Self-Efficacy", single_item("CORB10")), -->
<!--     composite("Perceived Response Efficacy", multi_items("CORB", 4:6), mode_B), -->
<!--     composite("Perceived Response Costs", multi_items("CORB", 7:9), mode_B), -->
<!--     higher_composite("Response Beliefs", c("Perceived Self-Efficacy", "Perceived Response Efficacy", "Perceived Response Costs"), weights =  mode_B), -->
<!--     composite("Distrusting Beliefs 1", multi_items("CODI", 1:9), weights = mode_B), -->
<!--     composite("Distrusting Beliefs 2", multi_items("CODI", 1:9), weights = mode_B), -->
<!--     interaction_term("Distrusting Beliefs 1", "Distrusting Beliefs 2", method = product_indicator), -->
<!--     composite("Knowledge", single_item("COKN")), -->
<!--     composite("Perceived Susceptibility", multi_items("COTB", 1:3)), -->
<!--     composite("Perceived Severity", multi_items("COTB", 4:6)), -->
<!--     higher_composite("Threat Beliefs", c("Perceived Susceptibility", "Perceived Severity"), weights = mode_B), -->
<!--     composite("Personal Moral Norm", multi_items("COPN", c(1,3))), -->
<!--     composite("Descriptive Norm", multi_items("CODN", 1:2), mode_B), -->
<!--     composite("Injunctive Norm", multi_items("COIN", 1:2), mode_B), -->
<!--     higher_composite("Subjective Norm", c("Descriptive Norm", "Injunctive Norm"), weights = mode_B), -->
<!--     composite("Behavioral Intention", multi_items("COBI", 1:3), mode_B) -->
<!--   ), -->
<!--   structural_model = relationships( -->
<!--     paths(from = c("Distrusting Beliefs 1*Distrusting Beliefs 2", "Knowledge"), to = c("Threat Beliefs")), -->
<!--     paths(from = c("Distrusting Beliefs 1", "Knowledge"), to = c("Response Beliefs")), -->
<!--     paths(from = c("Response Beliefs", "Threat Beliefs", "Personal Moral Norm", "Subjective Norm"), to = "Behavioral Intention") -->
<!--   ) -->
<!-- ) -->
<!-- # Estimate second model for f2 with construct excluded -->
<!-- motb1altex <- estimate_pls( -->
<!--   data = model$data, -->
<!--   measurement_model = constructs( -->
<!--     composite("Perceived Self-Efficacy", single_item("CORB10")), -->
<!--     composite("Perceived Response Efficacy", multi_items("CORB", 4:6), mode_B), -->
<!--     composite("Perceived Response Costs", multi_items("CORB", 7:9), mode_B), -->
<!--     higher_composite("Response Beliefs", c("Perceived Self-Efficacy", "Perceived Response Efficacy", "Perceived Response Costs"), weights =  mode_B), -->
<!--     composite("Perceived Susceptibility", multi_items("COTB", 1:3)), -->
<!--     composite("Perceived Severity", multi_items("COTB", 4:6)), -->
<!--     higher_composite("Threat Beliefs", c("Perceived Susceptibility", "Perceived Severity"), weights = mode_B), -->
<!--     composite("Knowledge", single_item("COKN")), -->
<!--     composite("Personal Moral Norm", multi_items("COPN", c(1,3))), -->
<!--     composite("Descriptive Norm", multi_items("CODN", 1:2), mode_B), -->
<!--     composite("Injunctive Norm", multi_items("COIN", 1:2), mode_B), -->
<!--     higher_composite("Subjective Norm", c("Descriptive Norm", "Injunctive Norm"), weights = mode_B), -->
<!--     composite("Behavioral Intention", multi_items("COBI", 1:3), mode_B) -->
<!--   ), -->
<!--   structural_model = relationships( -->
<!--     paths(from = c("Knowledge"), to = c("Response Beliefs", "Threat Beliefs")), -->
<!--     paths(from = c("Response Beliefs", "Threat Beliefs", "Personal Moral Norm", "Subjective Norm"), to = "Behavioral Intention") -->
<!--   ) -->
<!-- ) -->
<!-- # Bootstrap model for significance (500 samples) -->
<!-- bomotb1altort <- bootstrap_model(motb1altort) -->
<!-- sumbomotb1altort <- summary(bomotb1altort) -->
<!-- bomotb1altpi <- bootstrap_model(motb1altpi) -->
<!-- sumbomotb1altpi <- summary(bomotb1altpi) -->
<!-- ``` -->
<!-- ```{r tb1 results, echo = F} -->
<!-- # Assess impact using f² and significance -->
<!-- tb1ort <- nldf("Distrusting Beliefs", -->
<!--               "Threat Beliefs", -->
<!--               motb1altort, -->
<!--               motb1altex, -->
<!--               sumbomotb1altort) -->
<!-- tb1ort[3,3] <- "Quadratic Orthogonal" -->
<!-- tb1pia <- nldf("Distrusting Beliefs", -->
<!--               "Threat Beliefs", -->
<!--               motb1altpi, -->
<!--               motb1altex, -->
<!--               sumbomotb1altpi) -->
<!-- tb1pia[3,3] <- "Quadratic Product-Indicator" -->
<!-- tb1ort %>% -->
<!--   union( -->
<!--   tb1pia -->
<!-- ) %>% -->
<!--   datatable(rownames = FALSE, -->
<!--                      caption = "Comparative effects of Distrusting Beliefs on Threat Beliefs") %>% -->
<!--     formatRound(c(4:5), -->
<!--                digits = 3) -->
<!-- ``` -->

The Distrusting Beliefs - Threat Beliefs model can not be assessed.

## Effect of Knowledge on Threat Beliefs

<!-- # ```{r tb2 alt nonlinear estimate, echo = F, include = F} -->
<!-- # # Estimate alternate model with quadratic effect - HOCs as proxy -->
<!-- # motb2alt <- estimate_pls( -->
<!-- #   data = model$data, -->
<!-- #   measurement_model = constructs( -->
<!-- #     composite("Response Beliefs", multi_items("CCRB", c(1,4)), weights = mode_B), -->
<!-- #     composite("Distrusting Beliefs", multi_items("CCDI", 1:9), weights = mode_B), -->
<!-- #     composite("Knowledge1", single_item("CCKN")), -->
<!-- #     composite("Knowledge2", single_item("CCKN")), -->
<!-- #     interaction_term("Knowledge1", "Knowledge2", method = orthogonal), -->
<!-- #     composite("Threat Beliefs", multi_items("CCTB", 1:6)), -->
<!-- #     composite("Subjective Norm", c(multi_items("CCDN", 1:2), multi_items("CCIN",1:2))), -->
<!-- #     composite("Personal Moral Norm", multi_items("CCPN", c(1,3))), -->
<!-- #     composite("Behavioral Intention", single_item("CCBI1")) -->
<!-- #   ), -->
<!-- #   structural_model = relationships( -->
<!-- #     paths( -->
<!-- #       from = c("Distrusting Beliefs", "Knowledge1"), -->
<!-- #       to = c("Response Beliefs")), -->
<!-- #     paths( -->
<!-- #        from = c("Distrusting Beliefs", "Knowledge1*Knowledge2"), -->
<!-- #       to = c("Response Beliefs", -->
<!-- #              "Threat Beliefs") -->
<!-- #  -->
<!-- #     ), -->
<!-- #     paths( -->
<!-- #       from = c( -->
<!-- #         "Response Beliefs", -->
<!-- #         "Threat Beliefs", -->
<!-- #         "Personal Moral Norm", -->
<!-- #         "Subjective Norm" -->
<!-- #       ), -->
<!-- #       to = "Behavioral Intention" -->
<!-- #     ) -->
<!-- #   ) -->
<!-- # ) -->
<!-- # # Estimate second model for f2 with construct excluded -->
<!-- # motb2altex <- estimate_pls( -->
<!-- #   data = model$data, -->
<!-- #   measurement_model = constructs( -->
<!-- #     composite("Perceived Self-Efficacy", single_item("CORB10")), -->
<!-- #     composite("Perceived Response Efficacy", multi_items("CORB", 4:6), mode_B), -->
<!-- #     composite("Perceived Response Costs", multi_items("CORB", 7:9), mode_B), -->
<!-- #     higher_composite("Response Beliefs", c("Perceived Self-Efficacy", "Perceived Response Efficacy", "Perceived Response Costs"), weights =  mode_B), -->
<!-- #     composite("Perceived Susceptibility", multi_items("COTB", 1:3)), -->
<!-- #     composite("Perceived Severity", multi_items("COTB", 4:6)), -->
<!-- #     higher_composite("Threat Beliefs", c("Perceived Susceptibility", "Perceived Severity"), weights = mode_B), -->
<!-- #     composite("Benevolence", multi_items("CODI", 1:3)), -->
<!-- #     composite("Competence", multi_items("CODI", 4:6)), -->
<!-- #     composite("Integrity", multi_items("CODI", 7:9)), -->
<!-- #     higher_composite("Distrusting Beliefs", c("Benevolence", "Competence", "Integrity"), weights = mode_B), -->
<!-- #     composite("Personal Moral Norm", multi_items("COPN", c(1,3))), -->
<!-- #     composite("Descriptive Norm", multi_items("CODN", 1:2), mode_B), -->
<!-- #     composite("Injunctive Norm", multi_items("COIN", 1:2), mode_B), -->
<!-- #     higher_composite("Subjective Norm", c("Descriptive Norm", "Injunctive Norm"), weights = mode_B), -->
<!-- #     composite("Behavioral Intention", multi_items("COBI", 1:3), mode_B) -->
<!-- #   ), -->
<!-- #   structural_model = relationships( -->
<!-- #     paths(from = c("Distrusting Beliefs"), to = c("Response Beliefs", "Threat Beliefs")), -->
<!-- #     paths(from = c("Response Beliefs", "Threat Beliefs", "Personal Moral Norm", "Subjective Norm"), to = "Behavioral Intention") -->
<!-- #   ) -->
<!-- # ) -->
<!-- # # Bootstrap model for significance (500 samples) -->
<!-- # bomotb2alt <- bootstrap_model(motb2alt) -->
<!-- # sumbomotb2alt <- summary(bomotb2alt) -->
<!-- # ``` -->
<!-- # ```{r tb2 alt results, echo=FALSE} -->
<!-- # # Assess impact using f² and significance -->
<!-- # nldfdt("Knowledge", -->
<!-- #      "Threat Beliefs", -->
<!-- #      motb2alt, -->
<!-- #      motb2altex, -->
<!-- #      sumbomotb2alt) -->
<!-- # ``` -->

The Knowledge - Threat Beliefs model can not be assessed.

# Summary
Using the available tests, we did not find evidence for a quadratic influence of any of the exogenous variables.
