---
title: "Climate Crisis Iteration 2-d-2 (General) Endogeneity Evaluation"
output:
  distill::distill_article:
    toc: true
    toc_depth: 1
---

```{r setup, echo =FALSE, include=FALSE}
# Include libraries
library(tidyverse)
library(seminr)
library(DT)
library(htmltools)
library(lmtest)
library(nortest)
library(car)
library(distill)
library(targets)
source(here::here("R", "02_sem-evaluation.R"))
# Load models
tar_config_set(here::here("_targets"))
model <- tar_read("cc_model_2_d_2")
proxymodel <- tar_read("cc_model_2_d_2_proxy")
# Make summaries
# model summary cannot be generated because of f2 error
# summo <- summary(model)
sumprmo <- summary(proxymodel)
```

The code for the assessment of endogeneity using the Gaussian Copula approach comes from

Hult, G. T. M., J. F. Hair, D. Proksch, M. Sarstedt, A. Pinkwart, & C. M. Ringle (2018).
Addressing Endogeneity in International Marketing Applications of Partial Least Squares Structural Equation Modeling. Journal of International Marketing, 26(3), 1–21. https://doi.org/10.1509/jim.17.0151


# Test of parametricity

The Gaussian Copula approach can only be used if the independent variable in question is not normally distributed.
So we first test the distribution of the construct scores.
A significant p value (p < 0.05) for either the Shapiro-Wilk or the Lilliefors test indicates that the data is not normally distributed.

```{r distribution test, echo = FALSE}
# Find out if independent (i.e., exogenous) variables are non-normally distributed
# If yes, Gaussian Copula approach can be used.
testlist <- c(rownames(model$path_coef)[-5])
nntest <- data.frame('Variable' = character(),
             'Shapiro-Wilk W' = double(),
             'Shapiro Wilk p' = double(),
             'Lilliefors D' = double(),
             'Lilliefors p' = double())
for (i in 1:length(testlist)) {
  nntest <- nntest %>% base::rbind(nonnormaltest(model, testlist[i]),
                             deparse.level = 0)
}
nntest %>%
  datatable(
    caption = 'Results of normality tests',
    rownames = FALSE,
    options = list(pageLength = nrow(nntest))
  ) %>%
  formatRound(-1,
              digits = 3)
```
```{r distribution graph, echo = FALSE}
for (i in 1:length(testlist)) {
  nonnormalgraph(model, testlist[i])
}
```



All independent (or endogenous) variables are non-normally distributed.
Therefore, the Gaussian Copula approach can be used for all of them.


# Regression of Response Beliefs on Distrusting Beliefs

```{r gca rb, echo = FALSE, include = FALSE}
# Define Variables for easy access
DI <- model$construct_scores[,"Distrusting Beliefs"]
RB <- model$construct_scores[,"Response Beliefs"]

# Define number of bootstraps: 10.000 for reporting, 100 for testing
bootrounds <- 10000

# Estimate regression model
rbmodel <- lm(RB ~ DI)
summary(rbmodel)
bootrb <- Boot(rbmodel, R=bootrounds)
summary(bootrb)

# Make base df
rbdf <- data.frame(Construct = c("Distrusting Beliefs", "Copula Distrusting Beliefs"), 
                   Original.Model.Value = c(summary(bootrb)[2,5],NA),
                   Original.Model.p = c(bootSig(model$data, bootrb, 1, 0)[2],NA)
)

# Calculate copulas for independent variables
DI_star <- createCopula(DI)


# Calculate results with copula for Distrusting Beliefs
# Input is regular model + copula + 0
copuladirb <- lm(RB ~ DI + DI_star + 0)
summary(copuladirb)
# Bootstrap Standard Errors
bootcopuladirb <- Boot(copuladirb, R=bootrounds)
summary(bootcopuladirb)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopuladirb, 1,1)
# Attach to df
rbdf <- rbdf %>% cbind(
  DI.Co.Model.Value = c(summary(bootcopuladirb)[5]),
  DI.Co.Model.p = c(bootSig(model$data, bootcopuladirb, 1,1))
)

colnames(rbdf) <- c("Construct",
                    "Original model value",
                    "Original model p",
                    "DI copula model value",
                    "DI copula model p"
                    )
```

```{r gca rb table, echo = FALSE}
rbdft <- rbdf[,-1] %>% t() %>% as.data.frame()
colnames(rbdft) <- rbdf[,1]
rbdft %>% 
  datatable(caption = 'Results of the copula procedure for the regression of Response Beliefs') %>%
  formatRound(1:ncol(rbdft),
              digits = 3)
```

The Distrusting Beliefs copula is not significant, indicating that there is no endogeneity in the regression of Response Beliefs on its predictor.

# Regression of Behavioral Intention on its predictors

```{r gca bi, echo = FALSE, include = FALSE}
# Define Variables for easy access
BI <- model$construct_scores[,"Behavioral Intention"]
PN <- model$construct_scores[,"Personal Moral Norm"]
SN <- model$construct_scores[,"Subjective Norm"]

# Define number of bootstraps: 10.000 for reporting, 100 for testing
bootrounds <- 10000

# Estimate regression model
bimodel <- lm(BI ~ RB + PN + SN)
summary(bimodel)
bootbi <- Boot(bimodel, R=bootrounds)
summary(bootbi)

# Make base df
bidf <- data.frame(Construct = c("Response Beliefs", "Personal Moral Norm", "Subjective Norm", "Copula Response Beliefs", "Copula Personal Moral Norm", "Copula Subjective Norm"), 
                   Original.Model.Value = c(summary(bootbi)[2:4,5],NA,NA,NA),
                   Original.Model.p = c(bootSig(model$data, bootbi, 3, 0)[2:4],NA,NA,NA)
)

# Calculate copulas for independent variables - already happened
RB_star <- createCopula(RB)
PN_star <- createCopula(PN)
SN_star <- createCopula(SN)

# Calculate results with copula for Response Beliefs
# Input is regular model + copula + 0
copularbbi <- lm(BI ~ RB + PN + SN + RB_star + 0)
# summary(copularbbi)
# Bootstrap Standard Errors
bootcopularbbi <- Boot(copularbbi)
# summary(bootcopularbbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
# Attach to df
bidf <- bidf %>% cbind(
  RB.Co.Model.Value = c(summary(bootcopularbbi)[,5], NA, NA),
  RB.Co.Model.p = c(bootSig(model$data, bootcopularbbi, 3,1), NA, NA)
)

# Calculate results with copula for Personal Moral Norm
# Input is regular model + copula + 0
copulapnbi <- lm(BI ~ RB + PN + SN + PN_star + 0)
# Bootstrap Standard Errors
bootcopulapnbi <- Boot(copulapnbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input for bootsig is data, bootstrapped results, number of independent variables, number of copulas
# Attach to df
bidf <- bidf %>% cbind(
  PN.Co.Model.Value = c(summary(bootcopulapnbi)[1:3,5], NA, summary(bootcopulapnbi)[4,5],  NA),
  PN.Co.Model.p = c(bootSig(model$data, bootcopulapnbi, 3,1)[1:3], NA, bootSig(model$data, bootcopulapnbi, 4,1)[4],NA)
)

# Calculate results with copula for Subjective Norm
# Input is regular model + copula + 0
copulasnbi <- lm(BI ~ RB + PN + SN + SN_star + 0)
# Bootstrap Standard Errors
bootcopulasnbi <- Boot(copulasnbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Attach to df
bidf <- bidf %>% cbind(
  SN.Co.Model.Value = c(summary(bootcopulasnbi)[1:3,5], NA, NA,summary(bootcopulasnbi)[4,5]),
  # Input is data, bootstrapped results, number of independent variables, number of copulas
  SN.Co.Model.p = c(bootSig(model$data, bootcopulasnbi, 4,1)[1:3], NA,  NA, bootSig(model$data, bootcopulasnbi, 3,1)[4])
)


# Calculate results with copula for Response Beliefs and Personal Moral Norm
# Input is regular model + copula + 0
copularbpnbi <- lm(BI ~ RB + PN + SN + RB_star + PN_star + 0)
# Bootstrap Standard Errors
bootcopularbpnbi <- Boot(copularbpnbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Attach to df
bidf <- bidf %>% cbind(
  RB.PN.Co.Model.Value = c(summary(bootcopularbpnbi)[,5], NA),
  RB.PN.Co.Model.p = c(bootSig(model$data, bootcopularbpnbi, 3,2)[5], NA)
)

# Calculate results with copula for Response Beliefs and Subjective Norm
# Input is regular model + copula + 0
copularbsnbi <- lm(BI ~ RB + PN + SN + RB_star + SN_star + 0)
# Bootstrap Standard Errors
bootcopularbsnbi <- Boot(copularbsnbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
# Attach to df
bidf <- bidf %>% cbind(
  RB.SN.Co.Model.Value = c(summary(bootcopularbsnbi)[1:4,5], NA, summary(bootcopularbsnbi)[5,5]),
  RB.SN.Co.Model.p = c(bootSig(model$data, bootcopularbsnbi, 3,2)[1:4], NA, bootSig(model$data, bootcopularbsnbi, 3,2)[5])
)

# Calculate results with copula for Personal Moral Norm and Subjective Norm
# Input is regular model + copula + 0
copulapnsnbi <- lm(BI ~ RB + PN + SN + PN_star + SN_star + 0)
# Bootstrap Standard Errors
bootcopulapnsnbi <- Boot(copulapnsnbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
# Attach to df
bidf <- bidf %>% cbind(
  PN.SN.Co.Model.Value = c(summary(bootcopulapnsnbi)[1:3,5], NA, summary(bootcopulapnsnbi)[4:5,5]),
  PN.SN.Co.Model.p = c(bootSig(model$data, bootcopulapnsnbi, 3,2)[1:3], NA, bootSig(model$data, bootcopulapnsnbi, 3,2)[4:5])
)

# Calculate results with copula for Response Beliefs, Personal Moral Norm and Subjective Norm
# Input is regular model + copula + 0
copularbpnsnbi <- lm(BI ~ RB + PN + SN + RB_star + PN_star + SN_star + 0)
# Bootstrap Standard Errors
bootcopularbpnsnbi <- Boot(copularbpnsnbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
# Attach to df
bidf <- bidf %>% cbind(
  RB.PN.SN.Co.Model.Value = c(summary(bootcopularbpnsnbi)[,5]),
  RB.PN.SN.Co.Model.p = c(bootSig(model$data, bootcopularbpnsnbi, 3,3))
)

colnames(bidf) <- c("Construct",
                    "Original model value",
                    "Original model p",
                    "RB copula model value",
                    "RB copula model p",
                    "PN copula model value",
                    "PN copula model p",
                    "SN copula model value",
                    "SN copula model p",
                    "RB & SN copula model value",
                    "RB & SN copula model p",
                    "RB & PN copula model value",
                    "RB & PN copula model p",
                    "PN & SN copula model value",
                    "PN & SN copula model p",
                    "RB & PN & SN copula model value",
                    "RB & PN & SN copula model p"
                    )

```
```{r gca bi table, echo = FALSE, layout = "l-page"}
bidft <- bidf[,-1] %>% t() %>% as.data.frame()
colnames(bidft) <- bidf[,1]
bidft %>% 
  datatable(caption = 'Results of the copula procedure for the regression of Behavioral Intention') %>%
  formatRound(1:ncol(bidft),
              digits = 3)
```

The Personal Moral Norm copula is significant in all model constellations (p < 0.1).
However, adding the copula leads to a smaller path coefficient.
Other than that, none of the copulas is significant in any of the model constellations, pointing to no endogeneity in the relationships between Behavioral Intention and its predictors.
