---
title: "Climate Crisis Iteration 2-b-3 (Heating) Measurement Model Evaluation"
output: 
  distill::distill_article:
    toc: true
    toc_depth: 2
---

```{r setup, echo =FALSE, include=FALSE}
# Thought: It's possible that the targets pipeline would have to be included in each report
knitr::opts_chunk$set(echo = TRUE)
# Include libraries
library(tidyverse)
library(seminr)
library(DT)
library(htmltools)
library(distill)
library(targets)
# source(here::here("R", "00_data-wrangling.R"))
# source(here::here("R", "01_sem-estimation.R"))
source(here::here("R", "02_sem-evaluation.R"))
# Load models
tar_config_set(here::here("_targets"))
model <- tar_read("cc_model_2_b_3")
bootmodel <- tar_read("cc_model_2_b_3_boot")
bootfsmodel <- tar_read("cc_model_2_b_3_fs_boot")
ralist <- tar_read("cc_model_2_b_3_ra")
# Create summaries
summo <- summary(model)
sumfs <- summary(model$first_stage_model)
sumbomo <- summary(bootmodel)
sumbofsmo <- summary(bootfsmodel)
# Set seminr plot theme
thm <-
  seminr_theme_create(
    construct.compositeA.arrow = "backward",
    construct.compositeA.use_weights = FALSE,
    plot.adj = FALSE
  )
seminr_theme_set(thm)
```

# Model plots
## Original Estimate Path Model

This is the original estimate path model.

```{r plot model, echo=FALSE, layout="l-page"}
plot(model, title = "Original Estimate Model")
# p <- plot(model, title = "Original Estimate Model")
# save_plot(here::here("reports", "figures", "plot_cc_1_model.svg"))
# knitr::include_graphics(here::here("reports", "figures", "plot_cc_1_model.svg"))
```

## Bootstrapped Path Model

This is the bootstrapped path model.

```{r plot bootmodel, echo=FALSE, layout="l-page"}
plot(bootmodel, title = "Bootstrapped Model")
```

## Measurement Model Only

This is a path model showing only the measurement model components.

```{r plot mm model, echo=FALSE}
plot(bootmodel, measurement_only = TRUE)
```

```{r eval-df, echo = FALSE, include=FALSE}
# Base DF
evalmm <- get_mm_details(model)
```

# Evaluation of the mode A measurement model
```{r ref-eval prep, echo = FALSE, include=FALSE}
# get measurement evaluation
refevalmmbase <- measurement_evaluation_composite_A(model)

#Next step is HTMT
boothtmt <- get_htmt(bootmodel, bootfsmodel)
htmt_problems <- get_htmt_problems(boothtmt)

# Make final data frame
refevalmm <- refevalmmbase %>% 
  left_join(htmt_problems, by = "Construct")
```

## Convergent validity

Ideally, outer loadings (<font face="Symbol">l</font>) should be $\geq$ 0.70. Loadings below 0.40 are unacceptable. AVE should be > 0.50. 

## Internal consistency reliability

Both Cronbach's <font face="Symbol">a</font> and composite reliability <font face="Symbol">r</font><sub>c</sub> should be $\geq$ 0.60 and $\leq$ 0.90. The upper threshold of acceptability is 0.95.

## Discriminant validity

Discriminant validity is evaluated using the heterotrait-monotrait ratio (HTMT). The HTMT bootstrap confidence interval should not contain 1.

```{r ref-eval, echo=FALSE}
print_composite_A_evaluation_DT(refevalmm)
```

```{r ref-eval-HTMT,echo=FALSE, layout="l-page"}
#If there are problems with the HTMT, here is a detailed table
datatable(
  boothtmt,
  filter = 'top',
  options = list(pageLength = nrow(boothtmt)),
  rownames = FALSE,
  colnames = c(
    "Construct 1" = 1,
    "Construct 2" = 2,
    "Lower CI HTMT" = 3,
    "Upper CI HTMT" = 4
  ),
  caption = 'Details of the bootstrapped HTMT ratios'
) %>%
  formatRound(3:4,
              digits = 3) %>%
  formatStyle('Lower CI HTMT', backgroundColor = styleInterval(
    cuts = c(0.9, 1),
    values = c('#00', '#ffe5e5', '#ff9999')
  )) %>%
  formatStyle('Upper CI HTMT', backgroundColor = styleInterval(
    cuts = c(0.9, 1),
    values = c('#00', '#ffe5e5', '#ff9999')
  ))
```

As before, the HTMT bootstrap confidence intervals are only problematic for the Distrusting Beliefs lower-order constructs.
All others are below the critical thresholds.

## Results of the evaluation of the mode A measurement model

The mode A measurement model meets all quality criteria and can be retained as-is.

# Evaluation of the mode B measurement model

There are no regular mode B constructs left to evaluate.

# Evaluation of the mode B higher-order constructs

```{r hoc-eval base, echo=FALSE, include=FALSE}
forhocevalbase <- evalmm %>% filter(Mode == "HOCB") %>% rename(HOC = Construct, LOC = Indicator.or.LOC) %>% 
  mutate(Type = NULL, Mode = NULL)
```

## Convergent validity

Convergent validity cannot be evaluated.

## Collinearity

The variance inflation factor (VIF) should be < 5, ideally $\leq$ 3.

```{r hoc-for-eval col, echo = FALSE, include = FALSE}
hocvif <- data.frame(HOC = character(),
                    LOC = character(),
                    VIF = double())
for (i in 1:length(unique(forhocevalbase$HOC))){
  for (j in 1:nrow(filter(forhocevalbase, HOC == unique(forhocevalbase$HOC)[i]))){
    x = unique(forhocevalbase$HOC)[i]
    y = (filter(forhocevalbase, HOC == x))[j,"LOC"]
    hocvif <- hocvif %>% rbind(data.frame(HOC = x,
                              LOC = y,
                              VIF = unlist(summo$validity$vif_items)[paste0({{x}}, ".", {{y}})]))
  }}
```

## Significance and relevance

Indicator weights should be significant (t $\geq$ 1.65, bootstrapping CI does not include 0). Otherwise, the loading  <font face="Symbol">l</font> should be $\geq$ 0.50. Any positive indicator weight implies relevance.

```{r hoc-for-eval sar, echo=FALSE, include=FALSE}
# Make weights df
bthocwtbase <- rownames_to_column(as.data.frame(sumbomo$bootstrapped_weights)) %>% rename (
  Construct.Rel. = rowname,
  Original.Est.Wt. = "Original Est.",
  Bootstrap.Mean.Wt. = "Bootstrap Mean",
  Bootstrap.SD.Wt. = "Bootstrap SD",
  T.Stat.Wt. = "T Stat.",
  Lower.Bounds.CI.Wt. = "2.5% CI",
  Upper.Bounds.CI.Wt. = "97.5% CI"
)
bthocwtsplit <- base::strsplit(bthocwtbase$Construct.Rel., "  ->  ")
bthocwtsplit1 <- c()
bthocwtsplit2 <- c()
for (i in 1:length(bthocwtsplit)){
  bthocwtsplit1 <- append(bthocwtsplit1, bthocwtsplit[[i]][1])
  bthocwtsplit2 <- append(bthocwtsplit2, bthocwtsplit[[i]][2])
}
bthocwt <- bthocwtbase %>%
  cbind(data.frame(LOC = bthocwtsplit1, HOC = bthocwtsplit2)) %>%
  mutate(Construct.Rel. = NULL,
         Bootstrap.SD.Wt. = NULL,
         '0.in.Wt.CI' = ifelse(Lower.Bounds.CI.Wt. < 0 &  Upper.Bounds.CI.Wt. > 0, TRUE, FALSE),
         Lower.Bounds.CI.Wt. = NULL,
         Upper.Bounds.CI.Wt. = NULL)
# Make loadings df
bthocldbase <- rownames_to_column(as.data.frame(sumbomo$bootstrapped_loadings))[,1:2] %>% rename(
  Construct.Rel. = rowname,
  Original.Est.Ld. = "Original Est."
)
bthocldsplit <- base::strsplit(bthocldbase$Construct.Rel., "  ->  ")
bthocldsplit1 <- c()
bthocldsplit2 <- c()
for (i in 1:length(bthocldsplit)){
  bthocldsplit1 <- append(bthocldsplit1, bthocldsplit[[i]][1])
  bthocldsplit2 <- append(bthocldsplit2, bthocldsplit[[i]][2])
}
bthocld <- bthocldbase %>%
  cbind(data.frame(LOC = bthocldsplit1, HOC = bthocldsplit2)) %>%
  mutate(Construct.Rel. = NULL)

#Make final data frame
forhocevalmm <- forhocevalbase %>%
  left_join(hocvif[,2:3]) %>%
  left_join(bthocwt[,-5]) %>%
  left_join(bthocld)
colnames(forhocevalmm)[6] <- paste0("t(", nrow(model$data), ") (weight)")
```

```{r hoc-for-eval, echo=FALSE, layout="l-page"}
datatable(forhocevalmm,
          filter = 'top',
          options = list(pageLength = nrow(forhocevalmm)),
          rownames = FALSE,
          colnames = c("Weight (original estimate)" = 4, 
                       "Weight (bootstrap mean)" = 5,
                       "0 in CI (weight)" = 7,
                       "Loading (original estimate)" = 8
                       ),
          caption = 'Results of the mode B higher-order construct evaluation') %>%
  formatRound(c(3:6, 8),
              digits = 3) %>%
  formatStyle('VIF', backgroundColor = styleInterval(cuts = c(3,5), values = c('#00', '#ffe5e5','#ff9999'))) %>%
  formatStyle(colnames(forhocevalmm)[6], backgroundColor = styleInterval(cuts = c(1.649), values = c('#ffe5e5', '#00'))) %>%
  formatStyle('Loading (original estimate)', backgroundColor = styleInterval(cuts = c(0.499), values = c('#ff9999', '#00'))) %>%
  formatStyle('0 in CI (weight)', backgroundColor = styleEqual(c(1,0), c('#ffe5e5', '#00'), default = NULL))
```

The VIFs for the Distrusting Beliefs are above 3, but still below 5.
The weights for Distrusting Beliefs Integrity and Competence are non-significant, but with a sufficiently large loading, the constructs can be retained.
All other weights are significant and relevant.

## Results of the mode B higher-order constructs evaluation

All mode B higher-order constructs can be retained as-is.

# Results summary

The measurement model can be retained as is.
Structural model evaluation can commence.

```{r table-getter, echo = FALSE, include = FALSE}
write_excel_csv(refevalmm[,c(1:3,5:7,4)] %>% filter(Calpha < 1) %>% mutate(across(c(3:7),  round, 2)), "paper/mma_cc-2-b-3.csv",delim = ";")
#write_excel_csv(forevalmm[,c(1:2,4:8,10)] %>% mutate(across(c(3:8),  round, 2)), "paper/mmb_cc-2-b-3.csv", delim = ";")
write_excel_csv(forhocevalmm[,-7] %>% mutate(across(c(3:7),  round, 2)), "paper/mmhocb_cc-2-b-3.csv", delim = ";")
```
