---
title: "Climate Crisis Iteration 2-a-3 (Diet) Endogeneity Evaluation"
output:
  distill::distill_article:
    toc: true
    toc_depth: 1
---

```{r setup, echo =FALSE, include=FALSE}
# Include libraries
library(tidyverse)
library(seminr)
library(DT)
library(htmltools)
library(lmtest)
library(nortest)
library(car)
library(distill)
library(targets)
source(here::here("R", "02_sem-evaluation.R"))
# Load models
tar_config_set(here::here("_targets"))
model <- tar_read("cc_model_2_a_3")
proxymodel <- tar_read("cc_model_2_a_3_proxy")
# Make summaries
summo <- summary(model)
sumprmo <- summary(proxymodel)
```

The code for the assessment of endogeneity using the Gaussian Copula approach comes from

Hult, G. T. M., J. F. Hair, D. Proksch, M. Sarstedt, A. Pinkwart, & C. M. Ringle (2018).
Addressing Endogeneity in International Marketing Applications of Partial Least Squares Structural Equation Modeling. Journal of International Marketing, 26(3), 1–21. https://doi.org/10.1509/jim.17.0151


# Test of parametricity

The Gaussian Copula approach can only be used if the independent variable in question is not normally distributed.
So we first test the distribution of the construct scores.
A significant p value (p < 0.05) for either the Shapiro-Wilk or the Lilliefors test indicates that the data is not normally distributed.

```{r distribution test, echo = FALSE}
# Find out if independent (i.e., exogenous) variables are non-normally distributed
# If yes, Gaussian Copula approach can be used.
testlist <- c(rownames(summo$paths)[-c(1:2)])
nntest <- data.frame('Variable' = character(),
             'Shapiro-Wilk W' = double(),
             'Shapiro Wilk p' = double(),
             'Lilliefors D' = double(),
             'Lilliefors p' = double())
for (i in 1:length(testlist)) {
  nntest <- nntest %>% base::rbind(nonnormaltest(model, testlist[i]),
                             deparse.level = 0)
}
nntest %>%
  datatable(
    caption = 'Results of normality tests',
    rownames = FALSE,
    options = list(pageLength = nrow(nntest))
  ) %>%
  formatRound(-1,
              digits = 3)
```
```{r distribution graph, echo = FALSE}
for (i in 1:length(testlist)) {
  nonnormalgraph(model, testlist[i])
}
```



All independent (or endogenous) variables are non-normally distributed.
Therefore, the Gaussian Copula approach can be used for all of them.


# Regression of Response Beliefs on Distrusting Beliefs and Knowledge

```{r gca rb, echo = FALSE, include = FALSE}
# Define Variables for easy access
KN <- model$construct_scores[,"Knowledge"]
DI <- model$construct_scores[,"Distrusting Beliefs"]
RB <- model$construct_scores[,"Response Beliefs"]

# Define number of bootstraps: 10.000 for reporting, 100 for testing
bootrounds <- 10000

# Estimate regression model
rbmodel <- lm(RB ~ DI + KN)
summary(rbmodel)
bootrb <- Boot(rbmodel, R=bootrounds)
summary(bootrb)

# Make base df
rbdf <- data.frame(Construct = c("Distrusting Beliefs", "Knowledge", "Copula Distrusting Beliefs", "Copula Knowledge"), 
                   Original.Model.Value = c(summary(bootrb)[2:3,5],NA,NA),
                   Original.Model.p = c(bootSig(model$data, bootrb, 2, 0)[2:3],NA,NA)
)

# Calculate copulas for independent variables
KN_star <- createCopula(KN)
DI_star <- createCopula(DI)


# Calculate results with copula for Distrusting Beliefs
# Input is regular model + copula + 0
copuladirb <- lm(RB ~ DI + KN + DI_star + 0)
summary(copuladirb)
# Bootstrap Standard Errors
bootcopuladirb <- Boot(copuladirb, R=bootrounds)
summary(bootcopuladirb)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopuladirb, 2,1)
# Attach to df
rbdf <- rbdf %>% cbind(
  DI.Co.Model.Value = c(summary(bootcopuladirb)[1:3,5], NA),
  DI.Co.Model.p = c(bootSig(model$data, bootcopuladirb, 2,1), NA)
)

# Calculate results with copula for Knowledge
# Input is regular model + copula + 0
copulaknrb <- lm(RB ~ DI + KN + KN_star + 0)
summary(copulaknrb)
# Bootstrap Standard Errors
bootcopulaknrb <- Boot(copulaknrb, R=bootrounds)
summary(bootcopulaknrb)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopulaknrb, 2,1)
# Attach to df
rbdf <- rbdf %>% cbind(
  KN.Co.Model.Value = c(summary(bootcopulaknrb)[1:2,5], NA, summary(bootcopulaknrb)[3,5]),
  KN.Co.Model.p = c(bootSig(model$data, bootcopuladirb, 2,1)[1:2], NA, bootSig(model$data, bootcopuladirb, 3,1)[3])
)

# Calculate results with copula for both DI and KN
# Input is regular model + copula + 0
copuladiknrb <- lm(RB ~ DI + KN + DI_star + KN_star + 0)
summary(copuladiknrb)
# Bootstrap Standard Errors
bootcopuladiknrb <- Boot(copuladiknrb, R=bootrounds)
summary(bootcopuladiknrb)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootstrappedSignificance(model$data, bootcopuladiknrb, 2, 2)
# Attach to df
rbdf <- rbdf %>% cbind(
  DIKN.Co.Model.Value = c(summary(bootcopuladiknrb)[1:4,5]),
  DIKN.Co.Model.p = c(bootSig(model$data, bootcopuladiknrb, 2, 2))
)
colnames(rbdf) <- c("Construct",
                    "Original model value",
                    "Original model p",
                    "DI copula model value",
                    "DI copula model p",
                    "KN copula model value",
                    "KN copula model p",
                    "DI & KN copula model value",
                    "DI & KN copula model p"
                    )
```

```{r gca rb table, echo = FALSE}
rbdft <- rbdf[,-1] %>% t() %>% as.data.frame()
colnames(rbdft) <- rbdf[,1]
rbdft %>% 
  datatable(caption = 'Results of the copula procedure for the regression of Response Beliefs') %>%
  formatRound(1:ncol(rbdft),
              digits = 3)
```


Neither the Distrusting Beliefs nor the Knowledge copula is significant, indicating that there is no endogeneity in the regression of Response Beliefs on its predictors.


# Regression of Behavioral Intention on its predictors
```{r gca bi, echo = FALSE, include = FALSE}
# Define Variables for easy access
BI <- model$construct_scores[,"Behavioral Intention"]

# Define number of bootstraps: 10.000 for reporting, 100 for testing
bootrounds <- 10000

# Estimate regression model
bimodel <- lm(BI ~ RB)
summary(bimodel)
bootbi <- Boot(bimodel, R=bootrounds)
summary(bootbi)

# Make base df
bidf <- data.frame(Construct = c("Response Beliefs", "Copula Response Beliefs"), 
                   Original.Model.Value = c(summary(bootbi)[2,5],NA),
                   Original.Model.p = c(bootSig(model$data, bootbi, 1, 0)[2],NA)
)

# Calculate copulas for independent variables - already happened
RB_star <- createCopula(RB)

# Calculate results with copula for Response Beliefs
# Input is regular model + copula + 0
copularbbi <- lm(BI ~ RB + RB_star + 0)
summary(copularbbi)
# Bootstrap Standard Errors
bootcopularbbi <- Boot(copularbbi)
summary(bootcopularbbi)
# Calculate corrected p-values based on bootstrapped standard errors
# Input is data, bootstrapped results, number of independent variables, number of copulas
bootSig(model$data, bootcopularbbi, 1,1)
# Attach to df
bidf <- bidf %>% cbind(
  RB.Co.Model.Value = c(summary(bootcopularbbi)[,5]),
  RB.Co.Model.p = c(bootSig(model$data, bootcopularbbi, 1,1))
)

colnames(bidf) <- c("Construct",
                    "Original model value",
                    "Original model p",
                    "RB copula model value",
                    "RB copula model p"
                    )

```
```{r gca bi table, echo = FALSE, layout = "l-page"}
bidft <- bidf[,-1] %>% t() %>% as.data.frame()
colnames(bidft) <- bidf[,1]
bidft %>% 
  datatable(caption = 'Results of the copula procedure for the regression of Behavioral Intention') %>%
  formatRound(1:ncol(bidft),
              digits = 3)
```
The Response Beliefs copula achieves a significant p-value, however, adding the copula does not increase the size of the path coefficient.
Therefore, the copula will not be added to the final model.
