---
title: "Climate Crisis Iteration 2-c-3-a (Driving) Structural Model Evaluation"
output: 
  distill::distill_article:
    toc: true
    toc_depth: 1
---

```{r setup, echo =FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Include libraries
library(tidyverse)
library(seminr)
library(DT)
library(htmltools)
library(targets)
source(here::here("R", "02_sem-evaluation.R"))
# Load models
tar_config_set(here::here("_targets"))
model <- tar_read("cc_model_2_c_3_a")
bootmodel <- tar_read("cc_model_2_c_3_a_boot")
#sumplspre <- tar_read("cc_model_2_c_2_plspre")
# Make summaries
summo <- summary(model)
sumbomo <- summary(bootmodel)
# Set seminr plot theme
thm <-
  seminr_theme_create(
    construct.compositeA.arrow = "backward",
    construct.compositeA.use_weights = FALSE,
    plot.adj = FALSE
  )
seminr_theme_set(thm)
# My favorite operator
`%notin%` <- Negate(`%in%`)
```

# Model plots

## Structural Model Only

This is a path model showing only the structural model components.

```{r plot mm model, echo=FALSE}
plot(bootmodel, structure_only = TRUE)
```

# Collinearity

Collinearity is assessed using the variance inflation factor (VIF). VIF should be < 5, ideally $\leq$ 3.

There is no VIF information available.

# In-sample predictive power

In-sample predictive power is assessed using variance explained R². R² $\geq$ 0.75 indicates substantial in-sample predictive power, R² $\geq$ 0.5 moderate and R² $\geq$ 0.25 weak in-sample predictive power. R² $\leq$ 0.10 indicates a lack of model predictiveness.

```{r in-sample pp r^2, echo=FALSE}
r2 <- make_r2_table(summo) 
r2 %>% 
  datatable(
    filter = 'top',
    options = list(pageLength = nrow(r2)),
    rownames = FALSE,
    colnames = c('R²' = 2,
                  'R²adj' = 3),
    caption = 'In-sample predictive power') %>%
  formatRound(2:3,
              digits = 3) %>%
  formatStyle('R²', backgroundColor = styleInterval(cuts = c(0.1,0.249,0.9), values = c('#ff9999', '#ffe5e5', '#00','#ff9999')))
```

R² is below 0.25 , but not below 0.1.

# Effect size

Effect size f2² measures the impact of a predictor construct on an endogenous construct. f² $\geq$ 0.35 indicates a large effect, f² $\geq$ 0.15 a medium and f² $\geq$ 0.02 a small effect.

```{r effect size f^2, echo=FALSE}
f2 <- make_f2_table(model, summo)
f2 %>%
  datatable(
          filter = 'top',
          rownames = FALSE,
          colnames = c('f²' = 3),
          caption = 'Effect sizes') %>%
  formatRound(3,
              digits = 3) %>%
  formatStyle('f²', backgroundColor = styleInterval(cuts = c(0.019), values = c('#ff9999', '#00')))
```

The effect size indicates a medium effect.

# Out-of-sample predictive performance

Out-of-sample predictive performance cannot be evaluated.

# Significance and relevance of path coefficients

Significance is denoted by t-test and p values. A t of $\geq$ 1.65 signifies significance at the 10 % level, t $\geq$ 1.96 at the 5 % level and t $\geq$ 2.57 at the 1 % level.

```{r path-coeff, echo = FALSE, layout="l-page"}
pcdf <- make_pc_table(sumbomo)
datatable(pcdf,
          filter = 'top',
          rownames = FALSE,
          colnames = c("Original Estimate" = 3),
          caption = 'Relevance and significance of path coefficients') %>%
  formatRound(c(3:7, 9:10),
              digits = 3) %>%
  formatStyle(colnames(pcdf)[9], backgroundColor = styleInterval(cuts = c(1.649), values = c('#ff9999', '#00'))) %>%
  formatStyle('p', backgroundColor = styleInterval(cuts = c(0.049), values = c( '#00', '#ff9999'))) %>%
  formatStyle('0 in CI', backgroundColor = styleEqual(c(1,0), c('#ff9999', '#00'), default = NULL))
```

The path coefficient is significant and relevant.

# Summary table

```{r summary table-df print, echo = FALSE, layout="l-page"}
sumsm <- pcdf[,-c(3,5:7)] %>%
    left_join(f2) %>%
    rename('Path Coefficient Bootstrap Mean' = 'Bootstrap Mean',
           '0 in Path Coefficient CI' = '0 in CI',
           'Path Coefficient p' = 'p')
  colnames(sumsm)[5] <- paste0("Path Coefficient t(", nrow(model$data), ")")
datatable(sumsm,
          filter = 'top',
          options = list(pageLength = nrow(sumsm)),
          rownames = FALSE,
          colnames = c("f²" = 7),
          caption = 'Structural Model Summary') %>%
  formatRound(c(3,5:7),
              digits = 3) %>%
  formatStyle(colnames(sumsm)[5], backgroundColor = styleInterval(cuts = c(1.649), values = c('#ff9999', '#00'))) %>%
  formatStyle('Path Coefficient p', backgroundColor = styleInterval(cuts = c(0.049), values = c( '#00', '#ff9999'))) %>%
  formatStyle('0 in Path Coefficient CI', backgroundColor = styleEqual(c(1,0), c('#ff9999', '#00'), default = NULL)) %>%
  formatStyle('f²', backgroundColor = styleInterval(cuts = c(0.019), values = c('#ff9999', '#00'))) 
```

# Results summary

Personal Moral Norm as the last remaining predictor is both significant and relevant.
