---
title: "Climate Crisis Iteration 2-b-3 (Heating) Nonlinearity Evaluation"
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
---

```{r setup, echo =FALSE, include=FALSE}
# Include libraries
library(tidyverse)
library(seminr)
library(DT)
library(htmltools)
library(lmtest)
library(distill)
library(targets)
source(here::here("R", "02_sem-evaluation.R"))
# Load models
tar_config_set(here::here("_targets"))
model <- tar_read("cc_model_2_b_3")
bootmodel <- tar_read("cc_model_2_b_3_boot")
proxymodel <- tar_read("cc_model_2_b_3_proxy")
bootprmodel <- tar_read("cc_model_2_b_3_proxy_boot")
# Make summaries
summo <- summary(model)
sumbomo <- summary(bootmodel)
sumprmo <- summary(proxymodel)
sumboprmo <- summary(bootprmodel)
```

# Test for possible nonlinearity

First, we test for nonlinearity by applying Ramsey's RESET test for functional form to each partial linear model of the SEM.
As quadratic effects of higher-order constructs cannot (yet) be estimated using PLS-SEM, we also apply the test to the corresponding partial linear models of the proxy SEM without higher order constructs.
If the test statistic is significant, the respective partial regression might be nonlinear.

```{r reset, echo = FALSE}
# Make df with independent and response variable
varlist <- as_tibble(model$smMatrix)
# Make df
resetdf <- data.frame(
  'Independent variable' = character(),
  'Response variable' = character(),
  'Test statistic' = double(),
  'p' = double(),
  'DF 1' = double(),
  'DF 2' = double()
)
# Fill df
for (i in 1:nrow(varlist)) {
  resetdf <- resetdf %>% rbind(resetfun(varlist[[i, 1]],
                                        varlist[[i, 2]]))
}
resetdf %>%
  datatable(
    rownames = FALSE,
    caption = 'Results of Ramsey\'s RESET test for nonlinearity') %>%
  formatRound(c(3:4),
              3)
```
Using p = 0.05 as a threshold, there are no potential nonlinear effects.
Therefore, we did not test for a quadratic influence of any of the exogenous variables.
